---
title: "Project proposal"
author: "Postparty Experience - Willow, Tikyra, & Emmy"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readxl)
Postpartum_Experience_Survey_Responses_raw_data <- read_excel("../data/Postpartum Experience Survey (Responses) - raw data.xlsx")
#View(Postpartum_Experience_Survey_Responses_raw_data)
```


### 1. Introduction

The postpartum experience survey was created by Willow Gibson for a research project assigned in an undergraduate course titled "History of Midwifery and Women's Healthcare in the US" at College of the Atlantic in 2022. The survey was used to collect data about the postpartum experiences of anyone who gave birth between 2013 and 2023. The purpose of collecting this information was to observe the state of postpartum care in the US with aim of learning what gaps in care exist. 


Data was collected to through a Google form survey that was circulated via email and briefly on social media. This dataset contains 788 cases and 15 variables. One variable (`emails`) is not being included in our analysis as it refers only to the email addresses of survey takers that wished to learn more following analysis of the data.

We expect to add one or two additional variables to our dataset through the process of mutating the types of postpartum care into quality categories: good, better, and best. Definitions for these categories will be determined as we work to analyze our data. While we recognize that these definitions may be subjective in nature, we will be using published references to help us quantify what types of support are most fundamental to long term health vs what types of care are more optional.

For this project, our reserach question concerns the state of postpartum care in the US. We want to look more deeply at several of the relationships between variables in this dataset to evaluate some key aspects of the postpartum experience. Some of the questions we hope to explore are:

1. If we categorize postpartum care into "good", "better", and "best" categories, what quality of postpartum care is the average birther receiving?

2. Does quality of postpartum care vary from state to state?

3. Is there a correlation between age and quality of postpartum care received/offered?

4. What states require postpartum care to be covered by insurance? Does that requirement for coverage extend to Medicare recipients only, or does it extend to private insurance companies?

5. What types of postpartum support did respondents say were most critical to their household within the first year following birth? Are these types of care typically covered by insurance or are families paying for these services out of pocket?

6. Critical care vs ideal care - what are the differences?

### 2. Data

```{r rename-variables}
Postpartum_Experience_renamed_variables <- as_tibble(Postpartum_Experience_Survey_Responses_raw_data) %>% 
  rename( 
         `respondent` = `Timestamp`,
         `state` = `Which US state or country did you give birth in?`,
          `age` = `What was your age when you gave birth?`, 
      `birth_location` = `Where did you give birth?`,
        `informed_by` = `When you were pregnant, did your care provider give you information about postpartum care services?`,
    `other_info_sources` = `Did you learn about postpartum care services from any other sources?`, 
      `support_type`= `What types of support did you have access to postpartum?`,
         `provider` = `Who provided this support for you?`,
    `ins_covered_services` = `What postpartum care services did your insurance cover?`,
    `cost_factor` = `Was cost a factor in how much support you received?`,
        `if_insurance` = `If insurance covered postpartum care services, would you take advantage of it?`,
    `critical_support` = `What support was most critical to you/your household in first year following birth?`,
    `ideal_support` = `In a best case scenario, list all types of care and support you would need or want in the first year postpartum.`,
    `comments` = `Is there anything else you want to share about your postpartum experience?`,
    `emails` = `If you are open to follow up questions or want the results from this research project, please enter your email below.`)
```

```{r add-clean_critical_care-data}
Postpartum_combined <- bind_cols(Postpartum_Experience_renamed_variables, Clean_critical_care)

head(Postpartum_combined)

```


```{r excluding-international-entries}
Postpartum <- Postpartum_combined %>%
  filter(state != "Uk") %>%
  filter(state != "Norway") %>%
  filter(state != "Puerto Rico")
```

```{r dimensions}
dim(Postpartum)
```
Variables: 16

```{r glimpse}
glimpse(Postpartum)
```


### 3. Data analysis plan

The variables we will be visualizing to explore the research questions include (the numbers reference the questions listed in the introduction):

1. `respondent` and `quality`. The `quality` variable will be created through defining the good, better, and best categories of care.
2. `age` and `quality`.
3. `state` and `quality`.
4. `ins_covered_services` plus data from additional source(s)
5. `critical_support` , `respondent` , `ins_covered_services` , and `cost_factor` We may also want to create a new variable called `out_of_pocket` to quantify what services were being paid for outside of insurance coverage.
6. `critical_care` and `ideal_care`.

Other data needed:

- State by state postpartum insurance coverage requirements

- What factors are most important in postpartum care according to other sources (i.e. what services are equated with the best long term health outcomes)

- Distribution of quality of postpartum care across states

- Possible data source: Guarnizo, Tomás. “Doula Services in Medicaid: State Progress in 2022.” Center For Children and Families, Georgetown University Health Policy Institute, 2 June 2022, https://ccf.georgetown.edu/2022/06/02/doula-services-in-medicaid-state-progress-in-2022.

Types of graphs we may want to use:

 - Pie chart - to show the distribution of quality of care within the data.
 
 - Histograms - to compare experiences depending on `birth_location` 
 
 - More histograms - to show how different age groups experienced their care, filling with color for quality of care.

 - Bubble plot - to juxtapose `critical_support` and `ins_covered_services`

 - Density plots - to compare how experiences vary with age

 - Wordclouds - to visualize the repetitions within our qualitative data

 - Maps - to compare results between US states

 - Waffle plot - comparing `ideal_support` with `critical_support`
 


## Preliminary exploratory data analysis and cleaning strategies:

Visualization of filtered age distribution in California 

```{r stringr}
library(stringr)
```

```{r write-out-data-for-memo}
write.csv(Postpartum, "Postpartum.csv", row.names = FALSE)

# read_csv("data/Postpartum.csv")
```

```{r age-numeric-NAs}
#Postpartum_renamed_variables_US <- #Postpartum_renamed_variables_US |>
#  mutate(age = as.numeric(age))
```


```{r state-clean-up}
Postpartum_renamed_variables_US <- Postpartum_renamed_variables_US |>
  mutate(state = str_replace(state, "CO", "Colorado")) |>
  mutate(state = str_replace(state, "IA", "Iowa")) |>
  mutate(state = str_replace(state, "DC", "District of Columbia")) |>
  mutate(state = str_replace(state, "TN", "Tennessee")) |>
  mutate(state = str_replace(state, "MS", "Mississippi")) |>
  mutate(state = str_replace(state, "Mass", "Massachusetts")) |>
  mutate(state = str_replace(state, "Massachusettsachusetts", "Massachusetts")) |>
  mutate(state = str_replace(state, "RI", "Rhode Island")) |>
  mutate(state = str_replace(state, "NY", "New York")) |>
  mutate(state = str_replace(state, "Tennesee", "Tennessee")) |>

  #In order to correct specific mistakes/misspellings etc across the data frame.
#using stringr package  

  filter(state != "United States",
         state != "US",
         state != "USA")
```


```{r finding-other-NA-numerics}
#which(Postpartum$age > 100)

#`which` for identifying rows of a dataset.
```

```{r read-in-data}

Postpartum <- read.csv("Postpartum (1).csv")

```

```{r some-ages-california-distribution}
#Postpartum_renamed_variables_US %>%
#  filter(state == "California") %>%
#  ggplot(aes(x = age)) +
#  geom_histogram() +
#  xlim(0,50) #Additional outliers and NAs ignored for the sake of the visualization (still present in data frame)
```

Example of table:

```{r informed-by-count}
Postpartum |>
  count(informed_by) |>
  arrange(desc(n))

```

`Age` clean up:
```{r clean-age-with-laurie-help}
#Postpartum_by_child <- Postpartum_renamed_variables_US |> 
 # mutate(birth_age_year = str_replace_all(age, "\\d{4}", replacement = "")) |>
  #mutate(birth_age = map_chr(str_extract_all(birth_age_year, "\\d{2}"),  ~ str_c(.x, collapse = ","))) |> 
   #separate_longer_delim(birth_age, delim = ",") # this line of the code makes each birth age a separate entry in the spreadsheet
```

Map Draft

```{r map-draft-quality-by-state}
#library(maps)
#library(mapproj)
#library(tidyverse)

#states <- map_data("state")
#states <- rename(states, state = region)
#statessurveyed <- `states`

#Postpartum_renamed_variables_US <- #Postpartum_renamed_variables_US %>% 
# mutate(state = tolower(Postpartum_renamed_variables_US$state))

#We will need to finish creating the good/better/best categories for the `quality` variable to determine portions of quality of care before this map can be completed.

#Use lecture material from week 6 - leaflet

```



## 4. Data Ethics Review

The data ethics review section will be introduced in a separate class and is not part of the original proposal deadline.

