---
title: "Postpartum Experience"
author: "Postparty Experience"
output: html_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction

The postpartum experience survey was created by Willow Gibson for a research project assigned in an undergraduate course titled "History of Midwifery and Women's Healthcare in the US" at College of the Atlantic in 2022. The survey was used to collect data about the postpartum experiences of anyone who gave birth between 2013 and 2023. The purpose of collecting this information was to observe the state of postpartum care in the US, in addition to learning what gaps in care exist. 

Data was collected to through a Google form survey that was circulated via email and briefly on social media. 

Refer to the Markdown Quick Reference: Help -> Markdown Quick Reference. 

## 2. Data

Variables:


```{r}
# Code goes here
```

## 3. Data analysis plan

Text goes here.


```{r}
# Code goes here
```


## 4. Data Ethics Review

The data ethics review section will be introduced in a separate class and is not part of the original proposal deadline.

NOTES:
Want to see how the quality of postpartum care varies by state
Is there correlation between age and quality of postpartum care
how do we define "quality" of postpartum care" 
What states have postpartum care insurance cover options?
What supports did respondents say were most critical to their household within the first year?

