---
title: "Postpartum Experience"
author: "Postparty Experience"
output: html_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction

Data was collected to observe the state of postpartum care in the U.S. via Google sheets.

Refer to the Markdown Quick Reference: Help -> Markdown Quick Reference. 

## 2. Data

Variables:


```{r}
# Code goes here

Postpartum_Experience_Survey <- read_excel("../data/Postparum_Experience_Survey")
```

## 3. Data analysis plan

Text goes here.


```{r}
# Code goes here
```


## 4. Data Ethics Review

The data ethics review section will be introduced in a separate class and is not part of the original proposal deadline.

NOTES:
Want to see how the quality of postpartum care varies by state
Is there correlation between age and quality of postpartum care
how do we define "quality" of postpartum care" 
What states have postpartum care insurance cover options?
What supports did respondents say were most critical to their household within the first year?

