---
title: "Project proposal"
author: "Postparty Experience"
output: html_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

### 1. Introduction

The postpartum experience survey was created by Willow Gibson for a research project assigned in an undergraduate course titled "History of Midwifery and Women's Healthcare in the US" at College of the Atlantic in 2022. The survey was used to collect data about the postpartum experiences of anyone who gave birth between 2013 and 2023. The purpose of collecting this information was to observe the state of postpartum care in the US with aim of learning what gaps in care exist. 

Data was collected to through a Google form survey that was circulated via email and briefly on social media. This data set contains 788 cases and 15 variables. One variable (`emails`) in the data set is not being included in our analysis as it refers only to the email addresses of survey takers that wished to learn more following analysis of the data.

For this project, we want to look more deeply at several of the relationships between variables in this dataset. Some of the questions we hope to explore are:

1.Does quality of postpartum care vary from state to state?

2.Is there a correlation between age and quality of postpartum care received/offered?

3.If we categorize postpartum care into "good", "better", and "best" categories, what quality of postpartum care is the average birther receiving?
   (good defined as X, better defined as X, best defined as X) 

4.What states require postpartum care to be covered by insurance? Does that requirement for coverage extend to Medicare recipients only,or does it extend to private insurance companies?

5.What types of postpartum support did respondents say were most critical to their household within the first year following birth? Are these types of care typically covered by insurance or are families paying for these services out of pocket?

Refer to the Markdown Quick Reference: Help -> Markdown Quick Reference. 

## 2. Data

```{r dimensions}
dim(Postpartum_Experience_Survey_Responses_raw_data)
```


Variables:
we want inline coding here to add in dimensions

```{r rename-variables}
# Postpartum_Experience_Survey_Responses_raw_data <- Postpartum_Experience_Survey_Responses_raw_data %>% 
 # rename(Timestamp = timestamp,
# "Which US state or country did you give birth in?" =  state,
#
#
#
#
#
# )
```

## 3. Data analysis plan

Variables we will be visualizing to answer our questions:
1. `state`, "quality" variable good, better, best, will be fleshed out later
2. `age`, "quality" variable 
3. `timestamp` , "quality"
4. potential outside data needed
5. `critical_support` , `timestamp` , `covered_services` , `cost_factor`

other data needed:
other states postpartum care insurance laws

types of graphs we may want to use:
histogram
scatter plot
density plot
wordcloud
map


```{r}
# Code goes here
```


## 4. Data Ethics Review

The data ethics review section will be introduced in a separate class and is not part of the original proposal deadline.

NOTES:
Want to see how the quality of postpartum care varies by state
Is there correlation between age and quality of postpartum care
how do we define "quality" of postpartum care" 
What states have postpartum care insurance cover options?
What supports did respondents say were most critical to their household within the first year?
Exclusion of international entries for clarity

