---
title: "Project memo"
author: "Postparty Experience - Tikyra, Emmy, and Willow"
output: github_document
always_allow_html: true

---

This document should contain a detailed account of the data clean up for your data and the design choices you are making for your plots. For instance you will want to document choices you've made that were intentional for your graphic, e.g. color you've chosen for the plot. Think of this document as a code script someone can follow to reproduce the data cleaning steps and graphics in your handout.

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readxl)
library(stringr)
library(forcats)
library(gridExtra)
library(dplyr)
library(openintro)
library(countrycode)
library(ggpattern)
library(ggplot2)
library(RColorBrewer)
library(ggridges)
library(visdat)
#library(corpustools)
```

```{r read-in-data}

Postpartum <- read.csv("Postpartum.csv")
```


## Data Clean Up Steps for Overall Data

### Step 1: Rename variables

```{r rename-variables}

# This step occurred in the proposal, but we wanted to ensure all clean up steps were included in the memo.

# Postpartum_Experience_renamed_variables <- as_tibble(Postpartum_Experience_Survey_Responses_raw_data) %>% 
 # rename( 
    #  `respondent` = `Timestamp`,
     # `state` = `Which US state or country did you give birth in?`,
     # `age` = `What was your age when you gave birth?`, 
     # `birth_location` = `Where did you give birth?`,
    #  `informed_by` = `When you were pregnant, did your care provider give you information about postpartum care services?`,
    #  `other_info_sources` = `Did you learn about postpartum care services from any other sources?`, 
    #  `support_type`= `What types of support did you have access to postpartum?`,
    #  `provider` = `Who provided this support for you?`,
    #  `ins_covered_services` = `What postpartum care services did your insurance cover?`,
    #  `cost_factor` = `Was cost a factor in how much support you received?`,
    # `if_insurance` = `If insurance covered postpartum care services, would you take advantage of it?`,
    # `critical_support` = `What support was most critical to you/your household in first year following birth?`,
    # `ideal_support` = `In a best case scenario, list all types of care and support you would need or want in the first year postpartum.`,
    # `comments` = `Is there anything else you want to share about your postpartum experience?`,
    # `emails` = `If you are open to follow up questions or want the results from this research project, please enter your email below.`)
```

### Step 2: Manual translation of 'critical_care`

Each entry in `critical_care` was manually translated to match the terminology used in the multiple choice answers listed in the `support_type` variable. This resulted in a new "clean" version of `critical_care` variable called `critical`. The purpose of this cleaning step was to make the open ended answers easier to graph and compare to other variables. Consistent language allows for clearer and more meaningful visualizations.

```{r add-critical-column-to-dataset}

# This step occurred in the proposal, but we wanted to ensure all clean up steps were included in the memo.

# Postpartum_combined <- bind_cols(Postpartum_Experience_renamed_variables, Clean_critical_care)

# head(Postpartum_combined)

```

### Step 3: Clean `age`

```{r first-birth-age}
Postpartum <- Postpartum |> 
  mutate(first_age = substr(age, start = 1, stop = 2)) |> 
  mutate(first_age = if_else(first_age == "On", "35", first_age)) |> 
  mutate(first_age = as.numeric(first_age)) |> 
arrange(first_age) |> 

relocate(first_age, .after = age)

```

### Step 4: Clean `state`

```{r state-clean-up-names}
Postpartum <- Postpartum |>
  mutate(state = str_replace(state, "CO", "Colorado")) |>
  mutate(state = str_replace(state, "IA", "Iowa")) |>
  mutate(state = str_replace(state, "DC", "Washington, D.C.")) |>
  mutate(state = str_replace(state, "TN", "Tennessee")) |>
  mutate(state = str_replace(state, "MS", "Mississippi")) |>
  mutate(state = str_replace(state, "Mass", "Massachusetts")) |>
  mutate(state = str_replace(state, "Massachusettsachusetts", "Massachusetts")) |>
  mutate(state = str_replace(state, "RI", "Rhode Island")) |>
  mutate(state = str_replace(state, "NY", "New York")) |>
  mutate(state = str_replace(state, "Tennesee", "Tennessee")) |>

  #In order to correct specific mistakes/misspellings etc across the data frame.
#using stringr package  

  filter(state != "United States",
         state != "United states",
         state != "US",
         state != "USA")
```



```{r state-clean-up-first-entry}

Postpartum <- Postpartum |> 
  mutate(first_state = sub("(,|and|1|/|-|\\(|&).*", "", state)) |>
arrange(first_state) |> 

relocate(first_state, .after = state)

Postpartum <- Postpartum |>
  mutate(first_state = str_replace(first_state, "Arizona ", "Arizona")) |>
  mutate(first_state = str_replace(first_state, "Arkansas ", "Arkansas")) |>
  mutate(first_state = str_replace(first_state, "California ", "California")) |>
  mutate(first_state = str_replace(first_state, "california ", "California")) |>
  mutate(first_state = str_replace(first_state, "california", "California")) |>
  mutate(first_state = str_replace(first_state, "Colorado ", "Colorado")) |>
  mutate(first_state = str_replace(first_state, "First", "Tennessee")) |>
  mutate(first_state = str_replace(first_state, "Tennessee ", "Tennessee")) |>
  mutate(first_state = str_replace(first_state, "Indiana ", "Indiana")) |>
  mutate(first_state = str_replace(first_state, "Kentcky", "Kentucky")) |>
  mutate(first_state = str_replace(first_state, "Massachusetts ", "Massachusetts")) |>
  mutate(first_state = str_replace(first_state, "Massachusettsechusetts", "Massachusetts")) |>
  mutate(first_state = str_replace(first_state, "Michigan ", "Michigan")) |>
  mutate(first_state = str_replace(first_state, "Minesotta", "Minnesota")) |>
  mutate(first_state = str_replace(first_state, "Minnesotta", "Minnesota")) |>
  mutate(first_state = str_replace(first_state, "New York ", "New York")) |>
  mutate(first_state = str_replace(first_state, "New york", "New York")) |>
  mutate(first_state = str_replace(first_state, "North carolina", "North Carolina")) |>
  mutate(first_state = str_replace(first_state, "Oregon ", "Oregon")) |>
  mutate(first_state = str_replace(first_state, "Rhode isl", "Rhode Island")) |>
  mutate(first_state = str_replace(first_state, "Rhode Isl", "Rhode Island")) |>
  mutate(first_state = str_replace(first_state, "Rhode Islandand", "Rhode Island")) |>
  mutate(first_state = str_replace(first_state, "Texas ", "Texas")) |>
  mutate(first_state = str_replace(first_state, "Washington ", "Washington")) |>
  mutate(first_state = str_replace(first_state, "New jersey", "New Jersey")) |>
  mutate(first_state = str_replace(first_state, "wisconsin", "Wisconsin")) |>
  mutate(first_state = str_replace(first_state, "virginia", "Virginia")) |>
  mutate(first_state = str_replace(first_state, "Virginia ", "Virginia")) |>
  mutate(first_state = str_replace(first_state, "Maryl", "Maryland")) |>
  mutate(first_state = str_replace(first_state, "North dakota", "North Dakota")) |>
  mutate(first_state = str_replace(first_state, "pennsylvania", "Pennsylvania")) 
  
 unique(Postpartum$first_state)

```

### Step 5: Clean `support_type`

```{r rename-answer-with-commas}
Postpartum <- Postpartum |>
  mutate(support_type = str_replace(support_type, pattern = "In-home help with tasks like laundry, cooking, cleaning, and child care", "In-home help with care tasks")) 
```

```{r support-type-separate-longer}
Postpartum <- Postpartum |>
  separate_longer_delim(support_type, delim = ",")
```

```{r unique-support-types}
  unique(Postpartum$support_type)
```

```{r rename-support_type-open-ended-responses}
Postpartum <- Postpartum|>
  mutate(support_type = ifelse(support_type == " Mommy and me yoga and classes", "Other", support_type)) |>
  mutate(support_type = ifelse(support_type == " follow-up appointment with midwife; overnight doula (1 night per week)", "In-home wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " we didn’t have anyone else and I often wished we had someone to hold the both of us while we bonded with our baby.", "None of the above", support_type)) |>
  mutate(support_type = ifelse(support_type == " My partner was incredibly helpful. He handled all of the emotional support and meal and house prep and cleaning. However", "Other", support_type)) |>  
  mutate(support_type = ifelse(support_type == " any supports I had access to I had to find myself.", "NA", support_type)) |>
  mutate(support_type = ifelse(support_type == " As a note", "NA", support_type)) |>
  mutate(support_type = ifelse(support_type == "Yes there was a postpartum follow up but didnt seem like she did nuch other than repeat what she was reading off a pamphlet.", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |> 
  mutate(support_type = ifelse(support_type == " 1 PP appointment at 6 weeks", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " Virtual postpartum follow up visits due to COVID", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " In—home baby education", "Other", support_type)) |>
  mutate(support_type = ifelse(support_type == " Therapy (for PPD with second kid)", "Emotional support", support_type)) |>
  mutate(support_type = ifelse(support_type == " Postpartum doula", "In-home wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " Home visiting (Maine Families and public health nursing)", "In-home wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " I didn't really receive support. I know my pediatrician has lactation services but I didn't need.", "Lactation support", support_type)) |>
  mutate(support_type = ifelse(support_type == " Besides my required postpartum checkup and family care", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " Some of these were offered but not helpful. Saw a behaviorist bc my dad died right before birth but they just said I “seemed fine” and were no help", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " Ovia Parenting App coaches", "Other", support_type)) |>
  mutate(support_type = ifelse(support_type == " Baby was in NICU so we also had access to a social worker and classes with fellow nicu parents on development/feeding/etc", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " Lactation support pre-covid. Post covid nothing in hospital", "Lactation support", support_type)) |>
  mutate(support_type = ifelse(support_type == " Stay at home spouse", "Other", support_type)) |>
  mutate(support_type = ifelse(support_type == " Lactation support was virtual only due to pandemic", "Lactation support", support_type)) |>
  mutate(support_type = ifelse(support_type == " One postpartum appointment with my OBGYN", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == "Gave birth in 2020. Everything I thought I’d have access to was shut down", "None of the above", support_type)) |>
  mutate(support_type = ifelse(support_type == " Except for my second  was born March 2020. I had no follow up", "None of the above", support_type)) |>
  mutate(support_type = ifelse(support_type == " most of my concerns were ignored by my ob.", "None of the above", support_type)) |>
  mutate(support_type = ifelse(support_type == " the process wasn’t easy or clear. After my 6-week checkup", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " Had to seek out lactation help on my own", "Lactation support", support_type)) |>
  mutate(support_type = ifelse(support_type == " Ped PT and dentist for tie release + torticollis (for LO but her care is critical to my well being + BF journey)", "Other", support_type)) |>
  mutate(support_type = ifelse(support_type == "", "NA", support_type)) |>
  mutate(support_type = ifelse(support_type == " I probably could have had access to some of the other things on this list but didn't look into it", "None of the above", support_type)) |>
  mutate(support_type = ifelse(support_type == " Doula support", "In-home wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " I had access to lactation/new parent group but didn’t have the knowledge to go to them", "Lactation support", support_type)) |>
  mutate(support_type = ifelse(support_type == " Therapy for Anxiety", "Emotional support", support_type)) |>
  mutate(support_type = ifelse(support_type == " 6 week follow up pp with doctor", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " Lactation support was VERY hard to access", "Lactation support", support_type)) |>
  mutate(support_type = ifelse(support_type == " 1x nurse check-in over phone (through hospital)", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " Nighttime support night nurse", "Overnight help", support_type)) |>
  mutate(support_type = ifelse(support_type == " Postpartum doula and a night doula", "In-home wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " Therapist but not specializing in postpartum concerns", "Emotional support", support_type)) |>
  mutate(support_type = ifelse(support_type == " Family", "Family support", support_type)) |>
  mutate(support_type = ifelse(support_type == " Mental health therapy", "Emotional support", support_type)) |>
  mutate(support_type = ifelse(support_type == " but the second hospital I delivered at has a robust new parent program", "New parent groups - in person", support_type)) |>
  mutate(support_type = ifelse(support_type == " I didn’t attend any of the new parent groups", "NA", support_type)) |>
  mutate(support_type = ifelse(support_type ==" I probably had access to pelvic floor therapy but didn’t know about it in order to access it.", "Pelvic floor rehabilitation", support_type)) |>
  mutate(support_type = ifelse(support_type ==" Doula. Also", "In-home wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type ==" Emotional support", "Emotional support", support_type)) |>
  mutate(support_type = ifelse(support_type ==" None of the above", "None of the above", support_type)) |>
  mutate(support_type = ifelse(support_type ==" Grief support", "Grief support", support_type)) |>
  mutate(support_type = ifelse(support_type ==" Pelvic floor rehabilitation", "Pelvic floor rehabilitation", support_type)) |>
  mutate(support_type = ifelse(support_type ==" New parent groups - online", " New parent groups - online", support_type)) |>
  mutate(support_type = ifelse(support_type ==" Acupuncture", "Acupuncture", support_type)) |>
  mutate(support_type = ifelse(support_type ==" Massage or chiropractic", "Massage or chiropractic", support_type)) |>
  mutate(support_type = ifelse(support_type ==" New parent groups - in person", "New parent groups - in person", support_type)) |>
  mutate(support_type = ifelse(support_type ==" New parent groups - online", "New parent groups - online", support_type)) |>
  mutate(support_type = ifelse(support_type ==" Community meal train or other meal service", "Community meal train or other meal service", support_type)) |>
  mutate(support_type = ifelse(support_type ==" Hospital or office based wellness services and postpartum follow up appointments", "Hospital or office based wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " In-home wellness services and postpartum follow up appointments", "In-home wellness services and postpartum follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == "Hospital or office based wellness services and postpartum follow up appointments", "Hospital/office follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " In-home wellness services and postpartum follow up appointments", "In-home follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == " In-home help with care tasks", "In-home help with care tasks", support_type)) |>
  mutate(support_type = ifelse(support_type == "Pelvic floor rehabilitation", "Pelvic floor PT", support_type)) |>
  mutate(support_type = ifelse(support_type == "New parent groups - in person", "New parent groups", support_type)) |>
  mutate(support_type = ifelse(support_type == "New parent groups - online", "New parent groups", support_type)) |>
  mutate(support_type = ifelse(support_type == "In-home wellness services and postpartum follow up appointments", "In-home follow up appointments", support_type)) |>
  mutate(support_type = ifelse(support_type == "Community meal train or other meal service", "Help with meals", support_type)) |> 
  mutate(support_type = ifelse(support_type == "Grief support", "Emotional support", support_type))
  
```

```{r recheck-unqiue-entries}
unique(Postpartum$support_type)
```

### Step 6: Clean `birth_location`

```{r birth-location-cleanup}

Postpartum <- Postpartum |>
  mutate(birth_location = ifelse(birth_location == "Hospital, Was supposed to go to birth center", "Hospital", birth_location)) |>  
  mutate(birth_location = ifelse(birth_location == "At home", "Non-Hospital", birth_location)) |>
  mutate(birth_location = ifelse(birth_location == "Birthing Center attached to hospital", "Non-Hospital", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "Free standing birth center", "Non-Hospital", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "At home, I’m our car in an empty church parking lot", "Non-Hospital", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "Began at a free standing birth center, had to transfer to a midwife center at a hospital", "Hospital", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "Birthing center attached to a hospital", "Non-Hospital", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "Planned home birth, transferred to hospital", "Hospital", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "Free standing birth center, At home", "Non-Hospital", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "Hospital, Homebirth transfer to hospital csection", "Hospital", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "Natural birthing center attached to hospital", "Non-Hospital", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "Hospital based birth center (across a sky bridge)", "Non-Hospital", birth_location)) |>
  mutate(birth_location = ifelse(birth_location == "Hospital, Hospital x2", "Hospital", birth_location)) |>
  mutate(birth_location = ifelse(birth_location == "Hospital, began care at birth center all 3 times & transferred", "Hospital", birth_location)) |>
  mutate(birth_location = ifelse(birth_location == "Birthing center within a hospital", "Hospital", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "Hospital, Free standing birth center", "NA", birth_location)) |> 
  mutate(birth_location = ifelse(birth_location == "Hospital, At home", "NA", birth_location)) |>
  mutate(birth_location = ifelse(birth_location ==  "Hospital, Birth center room in the hospital", "NA", birth_location)) |>
  mutate(birth_location = ifelse(birth_location ==  "Hospital, Car", "NA", birth_location))
  
```

### Step 7: Clean `critical`

```{r rename-critical-clean}

Postpartum <- rename(Postpartum, "critical" = "critial_clean")

```

```{r relocate-new-critical-variable}
Postpartum <- relocate(Postpartum, critical, .after = critical_support)

```

```{r critical-separate-longer}

Postpartum <- Postpartum |>
   separate_longer_delim(critical, delim = ",")
   
```

```{r critical-unique}
unique(Postpartum$critical)
```

```{r critical-clean-up}
Postpartum <- Postpartum |>
  mutate(critical = ifelse(critical == " In-home help with care tasks", "In-home help with care tasks", critical)) |>
  mutate(critical = ifelse(critical == " Lactation support", "Lactation support", critical)) |>
  mutate(critical = ifelse(critical ==  " Pelvic floor PT", "Pelvic floor PT", critical)) |>
  mutate(critical = ifelse(critical ==  " Emotional support", "Emotional support", critical)) |>
  mutate(critical = ifelse(critical ==  " Help with meals", "Help with meals", critical)) |>
  mutate(critical = ifelse(critical ==  " Family support", "Family support", critical)) |>
  mutate(critical = ifelse(critical ==  " Other", "Other", critical)) |>
  mutate(critical = ifelse(critical ==  " New parent groups", "New parent groups", critical)) |>
  mutate(critical = ifelse(critical ==  " In-home follow up appointments", "In-home follow up appointments", critical)) |>
  mutate(critical = ifelse(critical ==  " Paid parental leave", "Paid parental leave", critical)) |>
  mutate(critical = ifelse(critical ==  " Overnight help", "Overnight help", critical)) |>
  mutate(critical = ifelse(critical ==  " Massage or chiropractic", "Massage or chiropractic", critical)) |>
  mutate(critical = ifelse(critical ==  " Acupuncture", "Acupuncture", critical)) |>
  mutate(critical = ifelse(critical ==  " family support", "Family support", critical)) |>
  mutate(critical = ifelse(critical ==  " Hospital/office follow up appointments", "Hospital/office follow up appointments", critical)) |>
  mutate(critical = ifelse(critical ==  " New parent group", "New parent group", critical)) |>
  mutate(critical = ifelse(critical ==  "Pelvice floor PT", "Pelvic floor PT", critical)) |>
  mutate(critical = ifelse(critical ==  " Pelvic floor rehab", "Pelvic floor PT", critical)) |>
  mutate(critical = ifelse(critical ==  " Unpaid parental leave", "Unpaid parental leave", critical)) |>
  mutate(critical = ifelse(critical ==  " in-home help with care tasks", "In-home help with care tasks", critical)) |>
  mutate(critical = ifelse(critical ==  "Pelvic floor rehab", "Pelvic floor PT", critical)) |>
  mutate(critical = ifelse(critical ==  "Emotial support", "Emotional support", critical)) |>
  mutate(critical = ifelse(critical ==  "Help with meal", "Help with meals", critical)) |>
  mutate(critical = ifelse(critical ==  "Lactation", "Lactation support", critical)) |>
  mutate(critical = ifelse(critical ==  "Lactatiom support", "Lactation support", critical)) |>
  mutate(critical = ifelse(critical ==  "Emototional support", "Emotional support", critical)) |>
  mutate(critical = ifelse(critical ==  "In-home help with child care", "In-home help with care tasks", critical)) |>
  mutate(critical = ifelse(critical ==  "In-home help wih care tasks", "In-home help with care tasks", critical)) |>
  mutate(critical = ifelse(critical ==  "Help with care tasks", "In-home help with care tasks", critical)) |>
  mutate(critical = ifelse(critical ==  "New parent group", "New parent groups", critical)) |>
  mutate(critical = ifelse(critical ==  "Child care", "In-home help with care tasks", critical)) |>
  mutate(critical = ifelse(critical ==  "Lacation support", "Lactation support", critical)) |>
  mutate(critical = ifelse(critical ==  "Sleep support", "Overnight help", critical))
```

```{r recheck-critical-entries}

unique(Postpartum$critical)

```


### Move to extra file??
```{r baseline}

#baseline <- c("Lactation support", "Pelvic floor rehabilitation",  "Emotional support",  "Hospital or office based wellness services and postpartum follow up appointments")

#better <- c("")

#best <- c("")

#baseline_pattern <- "lact|pelv|"

#Postpartum_support_type_clean <- Postpartum_support_type_clean |>
  #mutate(baseline = case_when(str_detect(support_type, pattern = regex(baseline_pattern, ignore_case = T)) ~ 1,
                         #    TRUE ~ 0)) 

#Postpartum_support_type_clean <- Postpartum_support_type_clean |>
  #mutate(baseline = case_when(support_type %in% baseline ~ 1,
                          #    TRUE ~ 0)) |>
  #mutate(service_category = case_when(support_type %in% baseline ~ "baseline",
                            #  TRUE ~ 0)) |>
  
 # relocate(baseline, .after = support_type)

#  Postpartum_support_type_clean |>
 # group_by(respondent, birth_age) |>
#  mutate(support_type_all = str_flatten(support_type, collapse = ", ")) |>
#  summarize(baseline_score = sum(baseline, na.rm = TRUE))
#  distinct(respondent, birth_age, .keep_all = TRUE) # we don't need this line, example only

#Postpartum_support_type_clean |>
# group_by(respondent, birth_age) |>
#  summarize(baseline_score = sum(baseline, na.rm = TRUE))|>
#  ungroup() |>
#  distinct(baseline_score)

```


## Plots

### Plot 1: Bar chart

```{r formal-care-type-bar-chart }

Postpartum |>
  filter(!is.na(support_type)) |>
  filter(support_type != "New parent groups - in person",
         support_type != "NA",
         support_type != "Overnight help",
         support_type != "Family support",
         support_type != "New parent groups",
         support_type != "In-home help with care tasks",
         support_type != "Other",
         support_type != "Help with meals") |>
  ggplot(mapping = aes(x = fct_rev(fct_infreq(support_type)), fill = support_type)) +
  geom_bar() +
  scale_fill_manual(
    values = c(
      "In-home follow up appointments" = "#d95f02",
      "Massage or chiropractic" = "#d95f02",
      "Acupuncture" = "#d95f02",
      "default" = "#66c2a5")) +
  #scale_fill_manual(
   # values = c(
    #  "Lactation support" = "#66c2a5",
     # "Emotional support" = "#66c2a5",
      #"Pelvic floor PT" = "#66c2a5",
    #  "Hospital/office follow up appointments" = "#66c2a5"))
     #  "default" = "darkblue")) +
  theme_bw() +
  theme(legend.position = 'none') + 
  coord_flip() +
  labs(title = "Formal types of Postpartum Care Accessed", 
       subtitle = "In the US Between 2013-2023 by Survey Respondents", 
       x = "Support Type", 
       y = "Number of Survey Respondents",
       caption = "The highlighted care types have been defined as care that increases the birthing parent and baby’s 
       physical and emotional wellbeing beyond baseline services."
       ) 

#we could add text on graph with geom_text() to indicate pink = higher quality services

#ggsave("example-postpartum-wide-2.png", width = 10, height = 4)
```

```{r formal-care-type-bar-chart-V2}

Postpartum |>
  filter(!is.na(support_type)) |>
  filter(support_type != "New parent groups - in person",
         support_type != "NA",
         support_type != "Overnight help",
         support_type != "Family support",
         support_type != "New parent groups",
         support_type != "In-home help with care tasks",
         support_type != "Other",
         support_type != "Help with meals") |>
  ggplot(mapping = aes(x = fct_rev(fct_infreq(support_type)), fill = support_type)) +
  geom_bar() +
  scale_fill_manual(
    values = c(
      "Lactation support" = "gold",
      "Emotional support" = "gold",
      "Pelvic floor PT" = "gold",
      "Hospital/office follow up appointments" = "gold",
      "default" = "darkblue"
    )
    ) +
  theme_bw() +
  theme(legend.position = 'none') + 
  coord_flip() +
  labs(title = "Formal types of Postpartum Care Accessed", 
       subtitle = "In the US Between 2013-2023 by Survey Respondents", 
       x = "Support Type", 
       y = "Number of Survey Respondents",
       caption = "The highlighted care types have been defined as the baseline care needed to prevent worst long term
       health outcomes for the birthing parent and baby."
       ) 

#ggsave("example-postpartum-wide-3.png", width = 10, height = 4)
```

```{r informal-care-type-bar-chart}
Postpartum |>
  filter(!is.na(support_type)) |>
  filter(support_type != "Lactation support",
         support_type != "Hospital/office follow up appointments",
         support_type != "Emotional support",
         support_type != "Pelvic floor PT",
         support_type != "Massage or chiropractic",
         support_type != "In-home follow up appointments",
         support_type != "Acupuncture",
         support_type != "None of the above") |>
  #count(respondent) +
  #mutate(percentage = n / sum(n) *100) |>
  ggplot(mapping = aes(x = fct_rev(fct_infreq(support_type)), fill = support_type)) +
 # geom_bar(stat = "identity") +
  theme_bw() +
  theme(legend.position = 'none') + 
  coord_flip() +
  labs(title = "Informal types of Postpartum Care Accessed", 
       subtitle = "In the US Between 2013-2023 by Survey Respondents", 
       x = "Support Type", 
       y = "Percentage of Survey Respondents",
     #  caption = "The highlighted care types have been defined as care that increases the birthing parent and baby’s  physical and emotional wellbeing beyond baseline services."
       ) 


```


### Plot 2: Ridge plot

```{r critical-ridge-plot}

Postpartum <- Postpartum |>
  filter(critical != "NA") |>
  filter(critical != "Duplicate entry")

ggplot(Postpartum, 
       aes(x = first_age, 
           y = critical,
           color = critical, 
           fill = critical)) +
  geom_density_ridges(alpha = .6) +
  scale_color_viridis_d(alpha = .6) +
  scale_fill_viridis_d() +
  scale_x_continuous(breaks = seq(from = 18, to = 44, by = 2)) +
  theme_minimal() +
  theme(legend.position = "none") +
  # need to re-order care types and potentially break it up by quality or formal/informal
  labs (title = "Most Critical Postpartum Care by Age of Birthing Person", subtitle = "what is the takeaway?", x ="Age During First Birth", y = "Care Type")

```
### Plot 3: Leaflet map

#### Data cleanup steps specific to plot 3

```{r create-quality_critical-variable}
# try mutating the group of care types into baseline/good, better, best with | between each care type

Postpartum <- Postpartum |>
  mutate(quality_critical = case_when(
    critical %in% c("Lactation support", "Pelvic floor PT", "Emotional support", 
                    "Hospital/office follow up appointments", "Unpaid parental leave") ~                      "baseline",
    critical %in% c("Paid parental leave", "In-home follow up appointments", 
                    "In-home help with care tasks", "Massage or chiropractic", 
                    "Acupuncture", "Overnight help") ~ "better wellbeing",
    critical %in% c("Help with meals", "New parent groups", "Paid parental leave", 
                    "Family support") ~ "community and long term support",
    TRUE ~ NA_character_
  ))

unique(Postpartum$quality_critical)
```

```{r relocate-quality_critical-variable}
Postpartum <- relocate(Postpartum, quality_critical, .after = critical)
```

```{r creat-quality_access-variable}
Postpartum <- Postpartum |>
  mutate(quality_access = case_when(
    support_type %in% c("Lactation support", "Pelvic floor PT", "Emotional support", 
                    "Hospital/office follow up appointments", "Unpaid parental leave") ~                      "baseline",
    support_type %in% c("Paid parental leave", "In-home follow up appointments", 
                    "In-home help with care tasks", "Massage or chiropractic", 
                    "Acupuncture", "Overnight help") ~ "better wellbeing",
    support_type %in% c("Help with meals", "New parent groups", "Paid parental leave", 
                    "Family support") ~ "community and long term support",
    TRUE ~ NA_character_
  ))

unique(Postpartum$quality_access)
```


```{r relocate-quality_access-variable}
Postpartum <- relocate(Postpartum, quality_access, .after = support_type)
```

```{r leaflet}
library(leaflet) ## For leaflet interactive maps
library(sf) ## For spatial data
library(RColorBrewer) ## For colour palettes
library(htmltools) ## For html
library(leafsync) ## For placing plots side by side
library(kableExtra) ## Table  output (in slides)
library(maps)

leaflet(Postpartum) |>
  addProviderTiles(provider = providers$OpenStreetMap) |>
  setView(lng = -80,
          lat = 34.5,
          zoom = 5) |>
  addPolygons(
    fillColor = ~pal74(Postpartum$regions),
    fillOpacity = 0.7,
    color = "white",
    opacity = 1,
    weight = 2)


#Postpartum |>
#ggplot(state_stats) +
 # geom_sf(aes(fill = "regions")) +
  #labs(title = "map",
   #    x = "Longitude",
    #   y = "Latitude",
     #  fill = "regions")


#ADD thingie to show stats
#labels <- sprintf("<strong>%s</strong><br/>%g births", 
               #   nc$county, nc$births1974) %>% lapply(htmltools::HTML)
#head(labels, 1)


```


```{r states-map}
map('state', fill = TRUE, col = palette())
```


```{r create-region-variable}

Postpartum <- Postpartum |>
  mutate(regions = case_when(
    first_state %in% c("Connecticut", "Maine", "Massachusetts", "New Hampshire", 
                       "New Jersey", "New York", "Pennsylvania", "Rhode Island",
                       "Vermont", "Delaware") ~ "Northeast",
    first_state %in% c("Illinois", "Indiana", "Iowa", "Kansas", "Michigan", "Minnesota",
                       "Missouri", "Nebraska", "North Dakota", "Ohio", "South Dakota",
                       "Wisconsin") ~ "Midwest",
    first_state %in% c("Alabama", "Arkansas", "Florida", "Georgia", "Kentucky",
                       "Louisiana", "Maryland", "Mississippi", "North Carolina", 
                       "South Carolina", "Tennessee", "Virginia", "West Virginia", 
                       "Washington, D.C.") ~ "Southeast",
    first_state %in% c("Texas", "Oklahoma", "Arizona", "New Mexico") ~ "Southwest",
    first_state %in% c("Alaska", "California", "Colorado", "Hawaii", "Idaho", "Montana",
                       "Nevada", "Utah", "Wyoming") ~ "West",
    first_state %in% c("Oregon", "Washington", "Idaho") ~ "Northwest",
    TRUE ~ NA_character_
  ))

unique(Postpartum$regions)

```

```{r testing thing}
install.packages("tm")
library(tm)
```



```{r relocate-regions-variable}
Postpartum <- relocate(Postpartum, regions, .after = first_state)
```

### Plot 4: Wordcloud

``` {r wordcloud-critical-care}

# install.packages("wordcloud2")
# install.packages("dplyr")
install.packages("tm", version = "0.7-13", dependencies = TRUE, repos = "http://cran.rstudio.com/")
# install.packages("viridis")
# install.packages("htmlwidgets")
# install.packages("webshot")


library(wordcloud2)
library(dplyr)
library(tm) 
library("viridis")
library(htmlwidgets)
library(webshot)

comments_text <- paste("Help with little things so I can nap while baby naps Help with meals and housework Help with cooking and cleaning, emotional support, trusted advice, chiropractic care Help with meals Lactation help New parents group & in home support Help with household tasks Hands on in house support in the initial weeks (with baby care and household tasks)
I would have benefitted from therapy and grief support, help with household tasks, better lactation support - instead I just ended up with postpartum depression Hands-down, having my parents retired and able to come over to help whenever I needed it. Close second was having quality, affordable child care available starting when my daughter was six weeks old, though we started her later. Childcare Help in the home Pelvic floor PT, lactation consultants IBLC - I waited far too long to access because I didn't realize insurance would cover LC outside a hospital setting I could have used mental health support, and pelvic floor therapy that was covered by insurance. Help overnight occasionally would have been amazing, or with the house, I felt like i was drowning. Childcare Overnights during the first few weeks, my partner being able to take leave for the first 5 weeks, friends and neighbors who helped with childcare, pet care, meals, and more, since we have no family in the area 
Lactation support People coming to visit, providing food and giving advice help with household tasks
Postpartum doula Helping with meals and cleaning in the first few months, lactation support (I would’ve had more than one visit with my second child of insurance covered it) Lactation support, mental health screening, pelvic floor therapy (but I didn’t receive them) The meal train made such a difference, but feeling more connected to more moms would have been helpful. It took me a while to attend an inperson support group and felt challenging, but I think that could have been made easier with prompting/encouragement.
Lactation support, meals and laundry
I got some support from my doula but not nearly enough! The one home visit was nice. One conversation with a lactation consultants. Definitely needed more support from family and friends, but everyone was scared of Covid and thought I should be too…
Lactation support, support with cooking, and a community to connect with for emotional support. 
Definitely lactation consultants, and I did PT for my hip pain, which was helpful. Also, meals and childcare support from friends/family. 
Sleep consultant
the community midwifery care model postpartum; hired in-home childcare
House cleaning, which was paid for by my parents for the first three months. 
follow up appointments with my midwife
We received horrific post parting support. I was gaslit and left in pain both emotional and physical 
Emotional support
Nanny
The meal train from friends. 
My spouse
Household help from spouse and family - meals and cleaning
Emotional support 
Family/Friends
Lactation Support
We had almost no support.
PT, general support at home from family (meals, child care, cleaning etc), support groups
In home help
Family assistance 
Emotional support 
Support from family members - helping with meals and laundry and taking care of my older child when the younger one was born 
Family and spouse support
Emotional/Physical/Lactation
Support at home, mental health support.
Trustworthy childcare
Food, support for sleep & self care 
Therapy. Psychological support 
The support from both things offered to be were not very helpful unfortunately 
I had terrible support w my first birth and that was a dark time. I learned how to advocate for myself with babies 2 and 3
Mental Health
Lactation support and massage
Probably emotional support but that was mostly my partner providing it
Mental health for my first. Household help for my second. 
Emotional and physical support for both spouse and I. Husband had to go back to work after two weeks, but we struggled hard. PPD hit me hard.
Lactation 
It would have helped my mental health 
I wish I had pelvic floor rehabilitation available at a better price, I really struggled for 2 years with pain but couldn’t afford thousands of dollars of it. I also wish I had more check ins with providers regarding mental health. I think I had PPA 6 months postpartum but couldn’t even get an appointment with my OB. 
Therapy 
Emotional, pelvic floor PT
N/a
Therapy, lactation consultant, family help
Lactation, emotional 
Therapy
Household chores (laundry, dishes, cleaning), meals, childcare for toddler once sibling arrived
Child Care
Emotional support of partner, friends and family 
Completing tasks around the house, babysitting, emotional support
Postpartum/emotional. I was a mess
I don’t know - sorry I had her in Dec 2019 and 3 months later the world shut down so I had nothing but me and my husband after the first 3 months. I think pelvic floor rehabilitation would have been great if I could have continued. Emotional support from husband and family and friends was important and I really appreciated my doula stopping by and just talking through breast feeding and the birth process after we got home before everything shut down. People dropping off food the first 2 months helped and people helping clean the house the first few months helped too.
I could have used any help really, I was kind of thrown to the wolves 
Medical care
House cleaning.
Lactation consultant, social media accounts for new moms/newborn advice
Lactation and in home support 
Emotional 
Meals, emotional support
Mental health and pelvic floor PT
Help with my other kids & home provided by family & friends
Lactation support and therapy
Childcare
We had very little support. In home support would have been very helpful, additional OB postpartum appointments and care would have been very helpful. Emotional support would have been helpful. 
In person support groups of lactation advisors and parenting support
Food/Household chores/lactation support
Meal service, new parent support group online 
Support group
Order in my house/ listening ear and shared experiences 
Lactation, Pelvic Floor, Counseling, Help at home
Therapy
Help from my sisters and MIL
We really didn’t have any honestly
Emotional & lactation 
Help with sleep
Learning how to breastfeed, keeping up with babies, work, & household
Childcare when returning to work.
Lactation support with an IBCLC (first) and Physical Therapy (second child)
Emotional support
Emotional and household chores
Safe!!!! Childcare for older child
Counseling-PPD/PPA
Emotional 
family offering in-home support 
I needed mental health support as I suffered from PPA
House cleaning, childcare 
Meal train (friends), in person support group
Household support - childcare, food, cleaning, etc. 
Lactation support
Medical care
Emotional support from family and friends
Spouse, social media group 
I would have benefited from professional mental health support-but did not receive/did not know how to access
Lactation would have been helpful. But also information about my traumatic birth. I had undiagnosed placenta accreta and hemorrhaged 2 weeks after my c-section.
Childcare
Lactation, child care
My hiking group helped me get outside and make friends
Emotional support and childcare assistance
Emotional, social 
Lactation and meal train 
Community building, we participated in a birthing and baby class at BirthRoots which is a parenting community building non-profit

Also lactation consultant
Therapist, family help with housework 
Lactation, pelvic floor, mental health
Lactation help and emotional support 
Emotional
Family being around for emotional support
In-home help, meal service, emotional support, PT
Pelvic floor physical therapy
Daily upkeep
Immediate support from mom/MIL with newborn those first couple of weeks. Supportive partner who took on helping with baby, supporting my breastfeeding journey, making meals, etc. Childcare support from family when we returned to work. This is support I had and I would consider critical.
Mental health- anxiety and depression support/medications
Lactation and help with household
Meal train. Lactation consultant. 
100% needed more babysitting, household support (chores)
Household help
Family support to help with household tasks
Would have loved more support in the home
Family and friends 
Child care 
Lactation help (wish I had more). Therapy. Assistance from my partner and parents. Other new mom friends!! 
Meals 
My mother helping with other children
All support needed more support overall
In home care (my mother moved in with us) 
Any household chores! Pelvic floor physical therapy and massage were helpful with pain 
Pelvic floor therapy, lactation services
My partner 
Help around the house and counseling
Didn’t have any 
Extra set of hands 
Family support
Lactation 
Nighttime support (postpartum doula who worked night shifts) and physical therapy 
Lactation support (I paid out of pocket) 
My MIL, lactation support, parent support groups 
Support with household tasks so I could focus on baby
Doula & nanny
Emotional support 
Breastfeeding support
Childcare
Meal train 
Emotional support only since this was my 2nd child
Lactation support
Emotional support and food dropped off by family
Help with child
had none
Mental health counseling 
Support from partner, paterniy/maternity leave from work
Child care
Spouse and family help
Mental health 
New parent groups 
Lactation support and mental health support. 
In-home childcare support
We didn’t have a lot of support, both because it was inaccessible financially but then we also lacked family/friend support due to COVID 19 and not having people around baby.
Emotional/mental
Breastfeeding emotional support
Lactation support
Lactation and housekeeping 
Therapy/ mental health services 
Childcare tied with lactation consultant 
Amazing support from my partner and having the choice to take some time off of work before returning. (I took 7 months unpaid and we scraped pennies to make it happen but it was crucial to my mental health.) those who are self employed like myself don’t even have FMLA. 
Meals and pelvic floor physical therapy 
Mental health
Cleaning, emotional support 
Lactation support 
Needed professional emotional support and lactation services: Hospital said they provided lactation services, but it was almost impossible to get in touch with the lactation consultants aver going home. 
For the first, therapy and meds for PPA, lactation support.  Second was postpartum doula support for logistics and emotional support. 
Childcare
Lactation, extra hands to help
Paid time off 
My partners support
exclusively pumping education, postpartum education and introducing solids. 
Having family support and help 
Meals
And PT
Household help 
Any support that you didn’t have to seek out/ask for help would have been welcomed
Getting everything else done--housework, food shopping, etc. I had much less time once I had my kids. 
Night nurse/doula, mental health care for PPD
Community- new parent group 
Childcare 
Family support (emotional, help with household tasks like cooking and laundry), and my husband had 12 weeks of fully paid parental leave
Talking with mol friends online
Childcare, therapy,  cleaning 
Paid maternity leave, physical therapy, lactation support, childcare 
Home support with household tasks 
Being able to reach anyone for support 
Lactation, mental support
My husband was/is the only person who provides any real support. He would do night feedings so I could rest until both children were sleeping through the night at 4.5 and 3.5 months. He made meals, helped with laundry, let me sleep in on weekends, and allowed me hours of child-free time when he was not working. 
Lactation support 
Help with tasks around the house and emotional support.
Family and friends—emotional and meals
Lactation support, friends Ava family helping with meals or just checking in on us mentally and emotionally. 
Family support 
Emotional and lactation support 
Lactation support, other supports I didn’t receive  
My sister helping out and coming over frequently 
Help with household chores so I could focus on baby
Ideally emotional support and support with tasks (cleaning or watching the baby so I could get a little sleep). 
Emotional support and household tasks 
My mom
Treatment from physician; support from workplace 
Therapy 
My spouse.  Minimal other support after 6 weeks 
Physical, emotional and mental support 
 
Emotional support 
Lactation support
Sleep. 
Mental health support would have been helpful 
Pelvic floor PT was crucial but other services ( doula, therapist eg) would have been very helpful
Meal/home help
Lactation support, mental health, body work, home derives, meal train  
Postpartum household tasks 
Hiring a housekeeper
Spouse 
Emotional support
Family support with managing household tasks, etc 
Paternity leave/spousal support 
Lactation support 
Emotional 
Childcare
Food already prepared
Lactation support
Spouse having some parental leave
Breastfeeding 
Lactation, pelvic floor PT, therapy, child care
Postpartum doula and pelvic floor pt
In home help
Emotional support for both of us. 
Help in the home
Child care and house work help from family 
Help with everyday tasks, meals, emotional support from husband 
Doctors/specialists 
I had none 
Money for childcare, money to hire out routine services like laundry and meals, money to pay full time childcare for older daughter while recovering w newborn, money for LC & massage therapist visits 
Household care would have been most helpful 
Emotional 
Ability to take maternity leave (12 weeks, paid using my sick/vacation time) and the small bit of paternity leave my husband could take (2 weeks). 
Lactation and doula
Extra hands to hold baby at times, meal support 
A night nurse for the first 2 months of baby’s life
Lactation support 
Help with child care 
In-home help with tasks like laundry, cooking, cleaning, and child care 
Breaks for naps since baby wasn’t sleeping much
Lactation
Lactation support 
Household chores, lactation 
Breastfeeding help, emotional support 
Lactation and in home nurse visit
Emotional 
Care for other children 
I really needed more leave from work - I used all my PTO for the birth and had none left all year for any illnesses (and there were many)
Emotional support and support from child’s pediatrician 
Lactation, housework/meals, childcare, Employer being very open and flexible for me to pump at work for a year +, supportive husband
Therapy. Lactation. 
Childcare 
Meals 
Lactation
Any support would have made a difference, especially after second birth
Lactation support and wellness 
All of it. My mental health was on the fritz from the sleep deprivation. I’m lucky I already had a therapist. Having an extra set of hands to help around the house was key to having my basic needs met (eating, showering, etc). The lactation consultant I found did house calls, which was amazing, but having to research for an IBCLC the week of my daughter’s birth was extremely stressful. 
Mental/emotional support. I would have loved to have access to pelvic floor therapy/physical therapy as well, but I couldn’t afford them and have no idea how to schedule that type of care (no one ever mentioned it as an option during my pregnancy or postpartum)
Lactation consultant
Maternity leave
My husband's support in taking on cleaning and cooking
Sleep consult, lactation consult, housekeeper
Emotional
Post partum depression, lactation, emotional support
New mom support groups 
My husband helping me in the middle of the night 
Emotional support 
Counseling
Mental health support 
Ability to access good childcare to be able to return work. 
Lactation/family members for child care 
?
Emotional and household support 
Emotional, household help, and breastfeeding 
My partner and social media postpartum accounts
Mental health 
Meal train. Pelvic floor therapy 
The in-person new mom group I attended at the hospital I gave birth to my first child provided the most direct information and support.
Household help
In home assistance with laundry and childcare, emotional support from spouse, therapy for PPD/PPA
Meals and house cleaning 
Support from my mom and other family members and friends was very important.
Emotional, I also wished that doctors would listen better, more communication when complications arose. 
My spouse support. 
Meal and household support 
Emotional support, lactation
In home support from fam
Family
Lactation support, sleep consultant 
Childcare 
Support from partner, family and friends
In home support with laundry and food, pelvic PT, massage, psychotherapy and lactation support 
Mental health would have been nice
Social support
Community support
Emotional, in home help, pelvic floor rehab 
Family and spouse support with baby-related tasks and house related tasks.
Help with household tasks, I was sleeping in 90 min increments due to triple feeding for three weeks, and I was a shell of a human when my partner went back to work after one week
Emotional support ; household tasks 
Paternity/ parental leave; screening and access to therapy for PPA 
Outsourcing tasks like cleaning and cooking
La leche league 
Access to our midwife 
Help during the newborn phase. Surgical support 3 months postpartum for delivery complications. 
Family/mother watching newborn. 
Household help
Lactation 
In-home help with tasks like laundry, cooking, cleaning, and child care. Emotional support
SAFE Childcare
I gave birth at the height of the pandemic in 2020 and had no support in-house apart from my husband because we were terrified of letting outsiders in & getting sick
Lactation support and also support from my mom who watched the baby so I could sleep occasionally.
Help at home
Lactation consultant, pediatrician 
I'm only 4mo pp currently, would be helpful to have someone take the baby sometimes so I could get other things done and/or have help with household tasks
Emotional support
Family medical leave 
Lactation/tounge tie. 
Familial support and it wasn’t a lot. 
Mental health support, help around the house
PP doula and an acupuncturist/pain specialist for neck/back pain from caring for LO
N/A
Family
Lactation and in person moms group
Childcare help and breast pump provision
Zoloft
Emotional support from other new moms, household task support from paid outside help, emotional support from spouse, lactation support 
Child care
My pelvic floor therapy and my therapist for PPD mitigation
Emotional support helped me through my PPD
I’m home help
Not sure
Medical care for baby and myself. 
Lactation services
Emotional, lactation
Splitting household/childcare with partner
Postpartum depression medication
Meal prep, household support, child care
Mental health, lactation
Friends and family, and structured/paid care (daycare).
Babysitting 
Lactation, mental health medication 
Child care (nanny) 
Spousal
Physical support - backup caregiving, help with household tasks, etc. All provided by family members. 
Childcare, family help with watching baby
Cleaning, meals, childcare for my other kids, watching the baby so I could sleep/ do self care / go to an appointment by myself 
I had none 
Lactation
Financial, childcare, mental health
Lactation support
A supportive spouse and a mom group I created in my neighborhood were critical for my first born during the first year. Also a lactation consultant coming to my house saved my nursing journey. 
Emotional support 
sleep support
Nanny and cleaning service
Lactation support 
Emotional; my birth was during the beginning of the pandemic and we were very isolated for safety reasons. Solidarity meant everything. 
Lactation support and emotional support
Mental health 
Family support in childcare
Household support, parenting skills 
Mental health
Part-Time Nanny to help with the other kids and to help with the newborn. Baby was small and lost weight. Had to pump extra to supplement. Needed someone to feed her while I pumped. She helped with the other kids or watched baby so I could take preschooler to school or spend 1:1 with my toddler.
Emotional and physical support of my partner
Lactation support, mental health supports, help with household from family, pelvic floor therapy would have been amazing but not offered 
Hospital provided weekly parent education and lactation support 
Family and therapy 
I wish I would have had post partum support for my second birth as I experienced post partum depression and still haven't been successfully referred to a therapist (my child is now 3)
Emotional 
Family (most critical second pregnancy as it was twins)
Secondary support (cooking, cleaning, etc)
Lactation support and mental health 
This was my second child, so I didn’t have the same concerns. With my first for sure lactation support. I felt like I was completely on my own. 
lactation 
I wish I had better mental health support. Had to fight for it and still lost it after the provider would no longer take my insurance.
Help with childcare
Emotional support / lactation / mental health for both myself and husband
New parent support 
I did not have maternity leave and it would have made a huge difference 
Nutrition 
Family
Family support- we didn’t have any
Pelvic Floor Physical Therapy—but I wish I knew about it sooner. 
Lactation support 
Emotional support
NICU nurse support, other NICU moms, financial support
Physical and mental
Any support would have been great. It was incredibly hard. 
We did not receive adequate support
Childcare
Lactation support
Pelvic floor PT, lactation, help with meal preparation 
Night doula, post partum doula, nanny
Lactation, in-home help from my family, therapist 
I needed someone to realize for me that I had postpartum anxiety and not just new mom worries.
Chiropractor support - I had really bad nerve pain after first birth.
Mental health support
Child care, meal support really any support would have been welcomed
Depression/stress support
Pelvic floor PT and PT for back pain So I could lift baby, also spouse help with household tasks and baby 
Spouse help
My mother helping with chores and cleaning and the baby at night
Mental health support, which I did not get. I suffered from postpartum anxiety and ocd.
Friends and family to step in when I was overwhelmed or needed a break. 
Family help
Peer support- moms group
Help with child care 
Lactation consulting, pelvic floor therapy, friends who forcibly came over and cleaned my house with love 
Emotional support
Social support, childcare
My mother being here to help for 3 months
Lactation consultant, emotional support 
Lactation, Help with food, and household chores, also the ability to sleep without interruption. 
My mom came over everyday, the home nurse visiting day 2 home from hospital. 
Child care, lactation, home cleaning/cooking
Lactation and tip sharing with other moms
Having a community, people to connect with 
PPA support
Affordable child care
Lactation support, evening / support so I could sleep
Family members bringing food and helping with the baby
Emotional support 
Meals and food were phenomenal to have assistance with as time for outdoor exercise for me to breathe, heal, feel better. Assistance with our oldest who was 4 yrs old with birth of second sibling was great to have. 
Mental health 
Support with household tasks/ helping me get sleep
I was pregnant and gave birth during the pandemic. It was a financially stressful time and health wise I was very concerned. A community or friends who could help would have been critical. 
Mental health and lactation 
Support at home- meals, cleaning, allowing me to nap
parenting group (https://www.peps.org/)
Lactation 
Physical therapy 
Childcare for my other 2 kids & husband home for first 6 weeks
Emotional support 
Lactation support, new mom group
Having family stay with us 
Physical therapy. Really needed a therapist or meds, but thought I could just work through birth trauma.
Postpartum doula, meal services
Emotional support from family
Lactation consultant 
Needed help with my older children. 
Mental health support following birth trauma
Family support 
Obgyn followups
Emotional support 
unknown 
Husband and parents 
My mom helping when able
Husband having 6 weeks paid off 
None, I needed more help 
Therapy, help with household chores, mom support groups, child care providers
Family support was absolutely vital.
Mental health therapy and PT (C-section, diastasis recti and pelvic floor)
Familial support 
Lactation (only one we were able to have)
Mental health support (which is non existent)
Emotional support and in home help
I wish we had new mom groups, lactation support, family to help care for older children, family to help when we were sleep deprived 
Domestic support. My mom came to help from out-of-state with the household responsibilities and babysitting. When she went home, it was challenging. My MIL helped every weekend with overnight care.
I had my mother during the first few weeks after giving birth. Everything else was pieced together over time by my own planning.
Meals and in home help
Emotional - therapy
Household/meal help (with my youngest as I then had 4 kids)
Lactation but wish I had had mental health,  household tasks, and night doula
Lactation consultant 
Emotional - breast feeding clinic 
I wish a had therapist, and support system 
Support from husband and lactation consultant
Counseling/emotional/mental, pelvic floor, lactation support, household help/food 
Support from family and friends - helping care for baby, give us breaks, provide meals, etc. 
Sympathetic friends and family
Lactation support, mental health care
Childcare, feeding support, Therapy for post partum anxiety
C section recovery - waited 3 years to start pelvic floor therapy because insurance wouldn’t cover it and had to pay out of pocket 
Help from family 
Lactation, pediatrician 
Unfortunately, my postpartum took place during Covid so I did not receive a lot of supports
In home help (laundry, cooking, cleaning)
Having a truly equal partner in my husband, the ability to quickly access mental health treatment when I needed it 
PPD&A. I needed a therapist and couldn’t find one. 
Lactation support, emotional support 
Lactation, help from family 
Lactation support, emotional support
Child care
Family help
Paid family leave
Emotional & household support in home
Childcare, help with chores
Leave from work and graduate school 
Help getting sleep
Lactation and emotional 
Mental health therapy and lactation support
Lactation support for oversupply/poor latch diet to suspected/self-resolving posterior tongue tie, & in-person parenting group
Psychologist 
In home help with daily tasks 
In-home help with meals, cleaning, household chores, etc
Household help, childcare, lactation support, 
Meal assistance, childcare for older siblings 
Emotional Support and massage
Housekeeping, dog walking, cooking, grocery shopping 
Mental health supports and physical support in home for home care tasks 
Emotional, mental. It felt like I was stuck in a bubble by myself, my mom and husband were my biggest supports.  But even though my husband didn’t fully understand my needs because I don’t think most people truly understand unless they’ve experienced childbirth and postpartum themselves. 
Lactation
, lactation, housework, 
More Emotional support would have been great. More help in general. 
Childcare 
Emotional/ mental health support
Sleep and lactation 
Lactation and the family nurse
Household help (didn’t receive any) and ongoing lactation support (only had one 20 minute appointment immediately after birth)
Cleaning person, therapist
Physical, help caring for baby to enable rest 
Pelvic floor physical therapy
Assistance with other household tasks and care of other children 
Mental health, pelvic floor rehab would have been helpful.
Therapy 
Partner support + therapy + house keeping
Sleep-training course (we paid for) and information regarding newborn/infant care on social media since we were first-time parents in March 2020 and didn’t have any in-person support from friends or family
Spouse home full time 
Family support
Doula support for me after first child and night doula after I had twins were; regular therapy sessions 
Help from spouse and family 
Childcare
Help with the house, food, other children
We didn't really have much of any, but an in-home postpartum care medical provider (murde or nurse midwife) would have made a huge difference the first year
Maven app and mom and sister staying over
Emotional/Mental 
I had basically none with my singleton birth (when I was 35) but learned more and we personally hired a postpartum doula for our twins’ birth (age 39). It saved our sanity. 
Being home for childcare 
I had horrendous post partum anxiety - not post partum depression but crippling anxiety thinking the baby was going to die constantly. It was really bad after every baby. If I could have afforded the therapy to deal with this, plus the childcare I would have needed to go to therapy I definitely would.
Mental Health support
Childcare so I could go to appointments 
IBCLC ran an in person new mom support group that got me out of the house & interacting with new moms in the same situation. It was a life line
Meal train 
Lactation, food would have been nice
Pelvic floor PT and lactation support 
Help with meals and child care
Family support- providing meals by setting up mela train among friends and neighbors and occasional care for the baby and, w my second child, the toddler. For the first month postpartum I leaned on my doula for advice w breastfeeding and my physical recovery. Therapy and meds for depression, which I already had pre pregnancy, were also crucial 
In home help. Emotional support
Emotional and cleaning. I wish I could do pelvic floor therapy 
Mental support, help with tasks
Family support 
Anti- depressants 
Emotional support 
Lactation assistance 
Therapy (for spouse), friends who brought food or gave us a break, parents who gave us a break 
Emotional and physical from emergency c-section 
Domestic support so I could have time to myself 
Family and friends 
Lactation, chiropractor, in home help with tasks and childcare including overnight care for newborn to give.a.break
I wish I could have had help with breastfeeding and sleep!
Meals, cleaning, breaks
Breastfeeding -exclusive pumper and no one educates you prior 
Housework help and cooking would have been most helpful 
Husband’s ability to help with baby.
In home help with baby care & household upkeep. Lactation
Family and friend support
Physical therapy/pelvic floor rehab and counseling
Being able to bond with our new baby while still being able to nourish and care for ourselves. 
Hospital grade breast pump and lactation support 
My mother coming to stay with us for 5 weeks (no family around us for 1000 miles)
Emotional and hands on help/care and lactation 
I gave birth February 2020. Once I left the hospital, zero support other than my husband. Postpartum appt cancelled due to covid restrictions and confusion. 
Postpartum depression and lactation services 
Talk Therapy
Parenting group 
Midwife, support group
Family support
Child care because we don't have family nearby and because maternity leave in the US is absolutely ridiculous and unacceptable. I don't know why all the women/moms in this country don't revolt against it. How can you be expected to go back to work when your baby is still breastfeeding every 2-3 hours and can't even hold their up properly yet!! All other developed nations give mothers the option to take 1 year off, at least your infant is a bit more independent by then and may or may not be breastfeeding anymore. 

Maternity leave in America is inhumane, it's anti-family, it's unjust. Pleaaaaase help us change that!!! Please!!! 
Psychiatry 
Family support
Lactation, in home help and meals
Social/family support 
Lactation
Lactation 
Husband stayed home to provide childcare 
I didn’t get the support I needed. Lactation was the most critical support that I did receive. 
Help from friends and family 
Wish I had mental health check ups
In home child care from my family
Child care to catch up on sleep and other things 
Psychologist and psychiatrist. Lactation consultant. Help with my baby at night. Help during the day so I could sleep. 
Pelvic floor PT, help from family 
Lactation consultant and pelvic floor and meal assistance
House help so I could rest, meals, laundry, etc. 
Emotional support from my doula and closest family/friends, having childcare for my older child so he was receiving additional care and attention in the early postpartum period, and having meals brought or prepped for us all. 
Physical in person help with every day things in the first few weeks by family was critical. 
Self sought pelvic floor therapy after my 2nd birth was crucial as well
Pelvic floor PT
Help with laundry and lactation 
IBCLC
My husband having one month of paternity leave, and then he was able to work remotely because of covid shortly after I gave birth. Having someone at home to be helpful between meetings was key. 
In home help
Lactation consultant 
Overnight care, mental health services 
Spouse
I needed support with housework and basic needs. Meals or errands or help with our dogs. 
In home support so I could sleep 
Strong relationship with my husband, therapy, ssri 
Should have been therapy but I didn't make myself a priority with my 1st like I'm doing with my 2nd
Our cleaning services 
Emotional and thankful to my husband for that because it was a very long and lonely journey 
Support of my husband in household chores and meals, and his emotional support
I was able to move in with family who helped me frequently with meals, helping with baby so I can sleep, helping wash pump parts and feed baby. 
Meal train, emotional support from spouse 
Pelvic floor rehabilitation , Lactation Support, In-Home help with tasks, in-home wellness services
Lactation. In home support like meals and childcare
Affordable childcare and paid maternity leave, I had leave partially paid, partially unpaid and took 13 weeks 
the care from my certified nurse midwife, as well as lactation consultation. i wish there had been accessible mental health and couples counseling as well 
Emotional and day to day support 
My friend started a Meal Train; this was the most valuable help in the immediate postpartum weeks.
Mental health support, physical support overnight 
Meds, physical recovery (massage, pelvic floor rehab) 
Therapy
Therapy, pelvic floor pt. The fact that birth is the only surgery that does NOT get an automatic PT referral in the hospital is bullshit, PT consults should be required. 
Family coming to clean, cook, etc. Being able to call my OB with any issues.
People showing up 
N/A
Maine Families and family 
In-house help, lactation support
Getting our nanny
Therapy/ medication
Help with baby so I could sleep
I needed therapy and did not know where to go for post partum mothers
Mental health would have been nice to know about and have.
Lactation support was most important to me 
Family help 
Emotional/mental
Assistance from family and lactation support
Emotional. I suffered from post partum anxiety and depression. 
Help around the house, childcare
Emotional support 
Lactation 
Our doula help. They made me feel like myself again. 
Lactation and sleep help
Therapy
My partners 20 week paid paternity leave. I would not have had more children had we not had that benefit!
Meals, pelvic floor PT, sleep support 
Family members washing dishes!!
Mental/physical 
Postpartum doula who know so much about newborns, cranial sacrum therapy, 
Emotional support, having a community of friends in a similar life stage. 
Therapy, 
Emotional support and physical help like laundry, cleaning, meals cooked.
Family support
Family help 
Family leave from work 
Family support, help with older kids, help with baby to get a break
Family providing childcare 
PT for my core and pelvic floor 
Provider/ familial 
Online “bumper” support group of moms who had babies the same month
Support from our family-mainly childcare 
Family support
Meals
PPD/PPA medicine 
Pelvic floor, therapy for PTSD from delivery 
Emotional support from spouse and my mother and every day support with household responsibilities such as cooking and cleaning
Counseling, lactation 
Not having support was really hard
Doula support. We did not have family in the area, my husband had ZERO paternity leave and we paid for all of the support out of pocket and I don’t know what I would have done without it 
Pelvic floor and parent-support groups, talk therapy
Family members helping out with meals and emotional support
Support with household tasks
Childcare
Lactation services and new mom support groups 
Help with household duties 
pelvic floor therapy 
Emotional support and sleep support
Lactation support. 
Emotional
Financial 
My family and friends supporting me; my therapist (online not covered by insurance)
Any food (cooking, delivery, groceries), cleaning, and dog walking were so important.
Physical recovery first and foremost and then PTSD/emotional support from birth trauma 
Support at home from partner and family
Lactation support/meal train
Pelvic floor therapy and ppa treatment 
Lactation consultant, pelvic floor PT
Emotional support from friends and family 
We didn’t get any. The worst time period of my life. 
Lactation support was very important. I could have used that with my second (my first child, born in Indiana at a birthing center, was the only child I had access to LS with). There were feeding issues I ran into with my second child that forced me to take less hours when I did return to work. 
Family support so I could sleep 
Childcare so I could return to work. 
Lactation support 
Lactation support for exclusive breastfeeding, physical therapist to rehabilitate core and pelvic floor
Emotional
Help with household tasks (cooking, laundry, etc.) and childcare so mom could sleep during the day
Wellness, emotional support, night nurse, sleep help
In home postpartum care, and continued in office care. 6 appointments within the first 6 weeks, plus phone and text access as needed.
An extra set of hands (to handle kids, make food, change laundry, etc)
House cleaning- my mom helped some 
My mom being close by to help with household tasks 
Physical rehabilitation and education apart from support with care which i had from family members 
Lactation/pumping. 
Chiropractic care 
I had c section so physical support as I could barely walk the first birth when I came home. They didn’t even send me home w enough painkillers. 
Emotional
I wish I had had better support in the form of mental health or household help including meals. I had good help for the physical aspect of birth but not much help otherwise.
Spousal support 
Spouse. Online support groups
Having my parents stay with us for a couple of weeks and my husband's paternity leave (quality postpartum therapy would have been good)
Help with baby when I (mom) was injured 
Lactation support, physical therapy
Household help with meals, so I wouldn’t have to cook; this was critical and was only fulfilled for the first week.  (I exclusively breastfed for three years with my first and five years with my second. The first three months of breastfeeding were very taxing on my body and mind. Good food is paramount. The MOST critical thing needed for me was adequate nourishment at small intervals without my needing to prepare it.) 
Being able to sleep and having someone take over watching the baby when I needed to rest. 
Emotional support would have been helpful. 
I needed more help with breastfeeding and pelvic floor therapy. I also struggled with maternity leave and having enough money to live. My time off was not clearly defined and my boss denied part of my leave while i was on maternity leave.
Emotional support, lactation support, family/friend support 
Food train
My mother in law folding my laundry 
Lactation consultant 
Pelvic floor therapy, help from family with other kids/meals while healing
Childcare, time for myself
Family support, mental support, physical therapy, and lactation
Child care and emotional support 
Mental, feeding the family, emotional support
Mental health/household support
Lactation
Having a postpartum doula / midwife home visits in first 8 weeks to identify and address jaundice & feeding issues between 2 week & 8 week baby wellness checks
Lactation and emotional house
Access to whatever mental health support I could receive, my PCP managing the aftereffects of my preeclampsia, my mom helping us 
Lactation, pelvic floor, Pp follow up and family taking care of us when we returned home
All of it. And more. 
Support with finances and work. Would have liked more maternity leave 
Lactation consultant and emotional support
We Googled a lot
Lactation support was helpful, but friends delivering meals was invaluable. Even having someone to wash dishes or hold the baby so I could shower 
Physical and emotional support. 
Family—childcare/relief, support with groceries or errands, cleaning and catching up on laundry, emotional support. 
Lactation
Time off and mental health care
Picking a phenomenal partner with whom to have a child; resources to order anything we needed from Amazon; amazing pediatricians; high quality infant care 
Support on transition back to work 
Night nurse 
Meals, emotional support, acupuncture 
Breastfeeding support
Help with meals
Breastfeeding Support
Childcare
family coming to stay since support network locally isn’t great
I wish we had more support for sleep. But the ability to not have to go back to work full time for myself and that my partner had a somewhat flexible job was the most crucial. As well was an online group I was part of and wished for an in person group. We had a very amazing lacatation counselor through pen bay we went to and she was so helpful and checked in alot
Meals, pelvic floor therapy, encapsulated placenta
My partner 
Emotional support, body work
Emotional support and the feeling of a community around us. It felt like we didn’t have that village everyone always bragged about. 
My partner 
Therapist and meal train 
Help with meals and some housework, lactation consultant 
Partner support, employer support
Postpartum doula WOULD have been the most critical
Postpartum doula WOULD have been the most critical
4 months in first year, so TBD! So far family support to help have someone else's practical support during the day and having overnight doula so we can sleep one night a week
Meal train
Lactation support IMMEDIATELY and recurring, twin club meal train for some early days,  my mom visiting after 2 weeks helping round the clock, dad helping when he visited later, We hired a nanny at 3 months so I could go back to work, and eventually (rarely) going to a therapist for postpartum depression care.  

This was not NEARLY enough support. 
Family support for child care, food, etc. 
Help from family
the support from other moms
Mealtrain in our first, acupuncture care in our second. My acupuncturist came to our home 
Spouse assistance, blogs on sleep training and a nanny once I returned to work 
Having my Mom close by was and is critical.
Lactation and support from other moms via friends and my postpartum support group")

corpus <- Corpus(VectorSource(comments_text))
corpus_clean <- corpus %>%
   tm_map(content_transformer(tolower)) %>% 
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>% 
  tm_map(removeWords, stopwords("en")) %>%
  tm_map(stripWhitespace) %>% 
  tm_map(removeWords, c("none"))

tdm <- TermDocumentMatrix(corpus_clean)

m <- as.matrix(tdm)

word_freqs <- sort(rowSums(m), decreasing = TRUE)

word_freq_table <- data.frame(word = names(word_freqs), freq = word_freqs)

colors <- viridis(nrow(word_freq_table), option = "D")

wordcloud2(word_freq_table, size = 0.5, color = colors)

#saveWidget(wc, "critcal-care-wordcloud.html")

```


```{r wordcloud-ideal-care}

install.packages("wordcloud2")
install.packages("dplyr")
install.packages("tm", dependencies = TRUE, repos = "http://cran.rstudio.com/")
install.packages("viridis")
install.packages("htmlwidgets")
install.packages("webshot")

library(wordcloud2)
library(dplyr)
library("viridis")
library("htmlwidgets")
library("webshot")
library(tm)

comments_text <- paste("Chiro, massage a portion of hours per week of nanny coverage, gym, etc Chiropractor, house help Lactation consultant, household help, childcare help, emotional support, chiropractic care/craniosacral therapy if needed, meal train for for the first few weeks 6+ months family bonding time, easier access to pelvic floor PT and suggested by provider, social groups with similarly aged kids for both mom and dad, pumping/lactation support, closer postpartum fu, massage. Lactation support, in home post Partum visits.
Pelvic floor, lactation consultant, sleep consultant, new parents group, night nurse
Support groups, lactation support, postpartum doula for help with tasks at home
Everything listed above. What I didn’t have was support and childcare to do self care things for me like massage, therapy, time with friends without baby
Access to therapy, body work especially pelvic floor support and advice on nursing posture, household services like cleaning and meal prep, lactation support, community grief space, parenting groups 
Everything above should be offered, but as for what I needed and wanted, the biggest was child care (family and facility) and people bringing me food. 
Lactation support, pelvic floor pt, house cleaning, meals, childcare, new parent peer group
A night nurse would have been wonderful in the first 6 months, just to offer support and shift burden from my husband and I 
Meals, therapy, lactation, PFPT 
Lactation consultant, doula, in-home help w/household tasks
Automatic pelvic floor (didn’t start this til way after because I didn’t know about it and thought everyone was slightly incontinent after birth)
Mental health
Lactation (I was using the wrong flange for pumping for a while)
Massage
Meal train was a huge help
Support exercising 
In person group aupport or a play group I gave birth in 2020 and everything was virtual
Everything mentioned in this survey
Everything listed in this survey
Lactation, pelvic floor, counseling, meal/cleaning/etc. And a nearby hands-on grandparent 
Medical, food, advice, lactation 
I was mostly happy with the Norwegian system although I think there should be better breastfeeding support in the first few days
Chef, more time from doula, longer maternity leave, local family support
Multiple covered lactation visits, help with driving (I had two c sections), help with childcare for my older kid when my 2nd was born, covered in-home visits from a therapist for both me and my partner
Lactation support, mental health screening, pelvic floor therapy, in home nurse support, meal train, chiropractor, new parent support groups
Grief and loss counseling was something that never crossed my mind but retroactively makes sense - I had a lot of myself to say goodbye to, at least temporarily, as I no longer had the freedom to come and go as I desired without baby and/or conversation with my partner.
In home lactation support, night time help, meal and laundry service, home nurse visits for mom and baby, Pelvic floor rehab, support group for moms and parents, mental health counseling support- the most helpful thing was someone telling me which providers to call. Finding someone to help and calling them when you are sleep deprived and have a newborn feels impossible. Being given names of lactation support people, and tongue tie specialists for my baby was critical for me. That came from my doula. My OBs did not have any specific recommendations for me, even for pelvic floor PT later on.  
In the first 6 weeks Meal train
Regular Postpartum doula visits
Help with household tasks 
Lactation support - not requiring a 4-6 week wait for an appointment 
Emotional support from family and friends 
Support for/from my partner
More follow up with midwife due to extended pp bleeding and pain
In the next months
Child care/Respite care Someone to just hold the baby while I take a shower and take basic care of myself 
Guidance for sleep and first foods
Pelvic floor PT
Acupuncture
Postpartum doula
IBCL
Meal train
Cleaning
I wish we had some postpartum doula support, especially to help navigate home chores and provide information on early baby development. I loved my in person support group, and which insurance had covered that. Additionally, all of the nursing/pumping supplies was super expensive. My pump and basic parts were covered by insurance, but I had to buy multiple flange sizes and other equipment that really added up. I also wish that bodywork had been covered by insurance. I would have really benefited from massage therapy and chiropractic care following birth. And home visiting for after birth visits!
Night nurse, cleaner, cook
Everything listed above!
Meal train, postpartum doula, weekly house cleaning, a mother’s helper 2-3x a week, pelvic floor PT, weekly chiropractic visits.
follow up and more continuous lactation consultation during my breastfeeding journey
Mental health services
Help with kids, cooking, cleaning, emotional support, occasional baby sitter. 
Therapy, exercise, massages, childcare for older child
Postpartum doula, lactation consultant, 
In home lactation help immediately following delivery, more frequent doctor checkups
Pelvic floor PT, lactation support, household support
Lactation support, emotional support, childcare, house cleaning 
More emotional/mental health support
Emotional/psychological, massage, lactation, increased wellness/health exams 
Postpartum doula, meal preparation, housekeeping, lactation consultant, pelvic floor therapy, post partum care for birth injuries (I had severe arm swelling from my IV; received no care, direction, or follow up from any healthcare provider); mental health services
PT, lactation support, physical recovery support before PT was approved at 6 weeks, home support (meals, childcare, cleaning), support groups
I’m home help, physical therapy, massage 
More paid time off especially for babies born premature. Lactation support
Anything and everything. Especially pelvic floor recovery, scar mobilization education, nutrition, child care, cleaning, early childhood education.
More time off work 
Night nurse
Pelvic therapy- the place I  could have went was 45 min away and I would have had to go once a week. That was too much time away from home 
If I had more childcare help and/or knowledge of these things : I would have had pelvic floor PT right away, help cooking and meal prep, more time for exercise, and all other tasks in home that felt overwhelming 
Emotional/physical/lactation 
Lactation, Mental Health, Meal Services, Pelvic Floor Rehab, Consistent follow up, wellness options at birth at after, maternity/paternity leave.
Lactation, pelvic floor rehab, childcare
Food, sleep support, lactation support, women’s wellness, therapy for depression & anxiety 
PT for physical therapy
Therapy for PPD/PPA 
Household help
Lactation support 
Mother support  group 
Postpartum mental health visits, in home help with tasks and in home wellness services 
Non judgmental lactation consultants at home (HATED the hospital ones), night nurses at least occasionally (or family who could give me like 4 hour chunks of sleep), pelvic floor PT, new mom support groups, homemaking tasks or watching toddlers (had very limited help w this even though I selected it above)
Mental Health, more check-ins earlier than 6 weeks, pelvic floor support (only learned about it on social media and currently having trouble pinning an appointment down).
I wish I had more support with breastfeeding, housekeeping, and basically everything that was listed above. 
Lactation support, more emotional support, support with household tasks
Pelvic floor rehab. Lactation consultant. Therapist. House cleaners. Meal train. Nighttime help occasionally. PATERNITY LEAVE-this is not just mom’s problem! 
Mental health support
Televisits and in-office visits with postpartum specialist or OBGYN
Physical support with house tasks, meal prep, etc. 
MENTAL HEALTH SUPPORT
Oh goodness, everything. I’d love it if I could have had lactation help, pelvic floor PT, emotional support, practical help (meals, cleaning)
Pelvic floor, lactation support, therapy, community groups 
Pelvic floor rehabilitation, mental health support every month for a year after birth, lactation support at home, doulas to help with laundry/cooking 
Help with household tasks, lactation consultant, someone to help with the baby at night because she would only sleep while being held which means my husband and I slept in shifts, pelvic floor pt, massage
PT
Lactation, pelvic floor rehab, emotional support, in-home help
Lactation consultant, therapy, meal delivery, cleaning service 
Lactation, emotional support, help with cleaning house
More medical visits for mom, in home visits from nurses, more community support, pelvic floor therapy, mental health therapy
Household chores (laundry, dishes, cleaning), meals, grocery shopping, childcare for toddler once sibling arrived, massage/body work — ideally weekly, in home by.a professional for at least the first few months, then periodically for the next year 
Pelvic, general strength, cleaning, night doula 
Emotional support, psychological counseling, lactation consultant, extra maternity leave time
Multiple ob visits, multiple pelvic pt, multiple mental health visits, postpartum/night doulas
Someone to be with me, tell me I’m doing ok, help me with the baby and chores. 
Lactation support, pelvic floor physical therapy, earlier follow up appointment just for mom, house and or food help, maybe therapy or parent group just to process changes
Night nurse, child care help, classes, connection with other new moms 
Household help childcare emotional support physical rehab
Housecleaning and food delivery. Even with my spouse at home I didn't feel like I could mentally handle breastfeeding with everything being a constant mess.
Wellness services postpartum (online preferred), pelvic floor rehab, massages
In home - laundry, cooking, cleaning, care for older sibling. Lactation. PT. Massage. Emotional support. 
Emotional, meals, PT, more health check ups, baby 101, childcare, sleep support, home suppport, financial support
All of the ones listed!
Home/childcare help, pt, mental health services, hormone monitoring postpartum 
Household, shopping, babysitting, emotional, physical like massage or acupuncture
Midwife to come to house for follow up appointment instead of going to doctor, especially for my one week wound check. Lactation support in home, therapy, paid time off for each parent. 
Night nurse, childcare, food delivery, paid maternity and paternity leave for 2 years
See above. I’m originally from Europe so when I hear the level of postpartum support my friends have over there, I really wish we had that in the US. I was astonished how neglected you are/feel postpartum vs prenatally. I would have loved in home support via in home doctors visits, assistance with cleaning/cooking, emotional support, longer/any parental leave for spouses so they can help more.
Postpartum visits from doula in home during first 2 weeks, ideally in home lactation consultation (to overlap for a period of time upon returning to work - like 6 months).  Ongoing mental health support.
Pelvic Floor Therapy, Counseling, Lactation Support, Meal Trains/Delivery, Household help
Not sure 
In home medical visits for me and baby. Minimum 16 week mat leave
Hired help with baby
pelvic floor PT, Counseling, Lactation Consultant, multiple OB checking (opposed to just one at 6 weeks) help at home
Talk therapy, processing birth with doula, pelvic floor PT, meals, childcare for older siblings, lactation support, in home massage, legal advice related to birth trauma 
Night nurse, massage therapist, counselor, meal delivery service, housekeeper 
PF therapy, help with meals and household, mental health support 
Lactation, counseling zooms, spouse home more (paternity leave/parent leave), childcare
Lactation/feeding, overnight support to get full night of sleep regularly 
Lactation, mental health, massage, stretching, 
The most important to me would be being able to take more time off work to care for my baby.
I’m home midwifery services; IBCLC visits; pelvic floor/physical therapy; mental health services, therapy (especially for traumatic births)
All of the things - emotional support, lactation, cleaning help and meal prep
Help with household and other children, PT, meals, emotional support from friends and family 
Inhome lactation, regular massagw when breastfeeding, pelvic floor therapy, 3 weeks postpartum doula, linger leave for spouse, online new moms group, a few emotional support therapy sessions
Lactation support with follow ups, weekly counseling sessions, night nurse 
Help managing multiple kids
lactation specialist, in home support, post partum OB visits, therapy for ppa/ppd
In-home doctor visits for the first 6 weeks (you shouldn’t have to take you or your child to the doctor), chiro adjustments, meal help, breastfeeding support, some kind of sleep support
Nutrition, healing, accupuncture, postpartum doula, night nurse, sleep education, lactation, emotional support, moms groups, paid/supported parental leave 
Help at home with household tasks, meals, & childcare (no local family & cost was prohibitive), mental health care & emotional support, bodywork, physical therapy, parent groups, sleep support, swaps for clothes & baby gear
More frequent Dr.  visits, lactation support, emotional support/therapy, new parent support groups, in home help, massage/chiropractic, physical therapy, pelvic floor therapy
In home support, meals, lactation, support groups
Pelvic PT, a doula, nighttime support for postpartum, home care visits
Emotional support, Meal train, help with housework , pelvic floor therapy, closer rehab post c section 
Doula, massage, in home help, nighttime support 
Lactation support, mental health support, additional OBGYN visits, pelvic floor therapy, help at home with cleaning cooking etc, mental health support for my husband, access to other new moms 
Lactation, PPD and PPA groups, in-home support like laundry, meals, etc.
Meal train, housekeeper, lactation consultant, pelvic floor therapy, childcare, massage/chiropractor, counselor, postpartum doula
Pelvic floor, childcare, maternity leave,  lactation support, mental health counselor
Mental health therapy/counseling
Lactation support
Meal train
Cleaning/housework help
Community activities/meet other moms
Pelvic floor therapy 
Pelvic floor evaluation, lactation services, emotional support access, access to childcare assistance
Emotional counseling, social group, home care/cleaning
Lactation, pelvic floor (as standard care), a nurse virtual visit at week 1/2 PP, normal 6 week visit, maybe a 3 month follow up. Meal train, postpartum doula. 
All of those listed in the previous multi-pick list
Night nurse, lactation, therapy, support groups 
Mehta health, physical check up-isle thyroid levels, iron levels. Pelvic floor PT, new mom support group
Household tasks help, emotional/mental health help, lactation support, physical care (massage, physical therapy etc.)
Lactation, child care for older children, meals, pelvic floor pt (then, not 6 years later when it was much harder to correct), massage/chiro, household chores, 
Lactation, home visit with lactation, nutrition, emotional, physical/exercise plan 
Lactation consultant, PT, at least 2 check-ups at dr/midwife’s office, in-home help, counseling (personal and couples), childcare assistance for older children
Pelvic floor PT, in-home postpartum and newborn checkups, in-home lactation consults, overnight doula, occasional nanny, food prep train, longer paid family leave 
Emotional, lactation, housekeeping
A non-judgmental and gentle sleep consultant, lactation support, easy access to support groups for breastfeeding and just new motherhood in general (maybe a group that starts in prenatal and carries over to postpartum), a meal train/more coordinated meal support, more mother/baby inclusive workout spaces and more flexible times for those classes, mom groups that are not just held during the “normal 9-5” work day for mothers who go back to work outside the home.
Someone to text/have casual conversation with when everything feels impossible. Someone to reach out. I didn’t like feeling like I had to ask for help. I wanted people to offer help, and not just I’ll hold the baby. I wanted to care for my baby, I didn’t want to do everything else (clean, cook, etc.)
Lactation, pelvic floor, emotional, household assistance 
Meal train, lactation consultant, OB appointment/postpartum check up, more info on breastfeeding 
Meals, night nurse, massage, acupuncture, in home doctor’s visits, more than one postpartum OB visit, having friends and family closer
Pelvic floor therapy, massage, home visits for first time mothers, lactation consult 
Mental health counseling, pelvic floor therapy, massage therapy (a true luxury). 
Emotional, household, pelvic floor PT
Cooking, cleaning, babysitting, pelvic floor therapy, LMHC, lactation consultant, more postpartum checkups 
Child care (financial stipend or free/low cost care)
Lactation help!!! it would be ideal if it were provided by my pediatrician’s office. New parents group. Night nurse help once a week. I’m home childcare for my toddler so she wouldn’t bring home daycare illnesses. Weekly postpartum counseling. Friendships with other mothers. 
Paid leave for partner, childcare, in home lactation support 
Counseling, lactation support, cleaning, meal service, 
Therapy, lactation, night nurse, peer support
Overnight care, lactation consultant, food preparation (for “yue zi” - one month confinement), acupuncture, massage, emotional support for new moms 
paid parental leave for me and my spouse; lactation support (in home and Virtual); meal train; house cleaner: massage; acupuncture; new parent group; postpartum doula for chores and sleep support and emotional support; pelvic floor physical therapy (in home ideal- It’s an hour drive in our rural community). 
In home follow up care appointments, help with cleaning, more pelvic floor therapy 
Pelvic floor, lactation, household help
Good, lactation, counseling, house chores
Household and meal support; emotional support; someone to come hold the baby so I could shower or just have a minute to myself; lactation support
Nanny, household manager, lactation consultant 
Parent support groups, 
Mental health 
Doula for labor, postpartum doula, lactation consultant, mom group, pelvic floor PT
Lactation support, emotional support with check ins, meals, household tasks, pelvic floor rehab
Sooner f/u with OBGYN, standard in home lactation support/RN f/u for mom and baby, postpartum doula, standard pelvic floor PT
Would love a situation like Taiwan where after hospital you check into a postpartum care hotel with nurse support for new parent training
Low cost childcare, more mental health focused care
Emotional support is my biggest one 
Lactation, meal service 
Childcare or staying at home for one year, breastfeeding support, pelvic floor rehab
Night nurse, cleaning/cooking, 1 year of maternity leave, massage, acupuncture, bodywork, therapy, chiropractic 
In home help, emotional support 
Pelvic floor, mental healthcare/talk therapy
Emotional, help with meals, pelvic floor therapy, OBGYN appointments beyond six weeks
 
Lactation, emotional support, cooking/cleaning, infant care
Doula services, in home checkups, mental health visits, in home lactation support 
Breastfeeding support groups, Mom groups, more follow ups with OBGYN, better family support - hands on help with baby/other kids
Child care, lactation, pelvic floor therapy, mom/support groups
Lactation consultation, pelvic floor therapy, in home cleaning help
Cleaning help, therapy
Longer term lactation support (not just the week post-birth), extended checkins for maternal mental health, pelvic floor therapy
Lactation support, meal trains, counseling sessions, mom support groups, coverage for specialized formula if needed for baby’s medical issues. 
Emotional/mental health support as I adjusted to becoming a mom; Pelvic floor rehab/PT; In-home follow-up appointments/Nurse visits; More in-office follow-up appointments
Lactation support, emotional support/evals, household cleaning, baby feeding support, childcare for other kids, meals and/or grocery shopping, there’s just so much. 
Therapy, support group 
Household help including cleaning, cooking and laundry, in house postpartum health visits, in home lactation support, massage, longer physical therapy, emotional support group of parents, paid time off for 6 weeks, leave from work for 1st year, childcare for other older children 
Lactation support. Proper parental leave. In home wellness visits. Therapy. 
Pelvic PT, Doula, Lactation, Pumping expert, psychological assistance, 
Post-partum doula/ in-home support for the mother/baby dyad to bond and rest, broader community care & supports (we have no village and it sucks), baby-friendly mental health services (both individual and group care), greater access to medical/obstetrical care beyond 6 wk postpartum appointment, federal caregiver income to support parents staying home to raise their babies, nighttime support in the fourth trimester so mother can rest & heal 
Paid parental leave, lactation consultant, pelvic floor therapy, earlier postpartum anxiety/depression screening
Too may to list. In home support of all kinds though. The last thing a newly postpartum person should have to do is strap themselves and their baby into a car to go anywhere for any reason. 
More of a community, more support after the newborn stage too, help with older kids
Doula, in-home lactation help, in-home help with everyday tasks, support group
Therapy, emotional support, cleaning, paid leave
Emotional support, paid cooking support, pelvic floor rehabilitation, and sleep doula
Lactation, home cleaning, mental health, new parent, massage, more follow-ups
Pelvic floor PT, CBT, meal support, parenting education, financial means to stay home longer, lactation support, 
Childcare, meal prep, pelvic floor therapy, psychotherapy, home cleaning, night nurse 
All of the above
Paid time off. Midwife/nurse home visits, meal trains, lactation consultants. 
More frequent check ins from a health professional at home would be amazing. Counseling/therapy. Meal service. Free lactation consulting. New mom meeting group to discuss postpartum changes. 
Breastfeeding, help with physical recovery after c-section, nurses assistance for the first 12 weeks, meal prepping and mental health support. 
Family support, postpartum doula to help with sleep, lactation support, more than 1 postpartum follow up with care providers, massage, chiropractic 
Counseling, in-home RN support, home visits from pediatrician, pelvic floor pt, church support via meal trains/laundry, more postpartum visits with obgyn or midwife 
Household help, pelvic pt, postpartum fitness education 
Lactation, emotional support, in home tasks, pelvic floor rehab, additional doctors office check up
Housework, mental health support, pelvic floor therapy/chiropractic care 
Doula, night nurse, lactation consultant therapy for mental health, paid maternity leave 
Pelvic floor, therapy (for my husband too!), lactation help 
Doula, nanny, house cleaner/cook. My spouse to have more and flexible time off.
Family/spouse support, IBCLC, counseling, pelvic floor therapy, new parents group support, adequate midwifery follow up
Pelvic floor rehab, postpartum doula, therapy
Pelvic floor rehabilitation, physical therapy, therapy, childcare, lactation support, paid leave 
4+ months paid maternity leave, childcare that covered 12+ hour shifts in the hospital, pelvic floor PT, mental health care, in home help like meal services etc, follow up care. 
More Emotional support and additional after birth visits with practitioner 
Lactation, mental wellness, pelvic rehab 
Pelvic floor, mental health, new mom shpport
Meal prep, emotional support, proactive navigation of health insurance offerings, laundry service, more postpartum check-ins with ob/gyn instead of 6 weeks, doula/infant care specialist 
All of the types of support listed above 
Lactation support, therapy, pelvic floor therapy, continued help around the house & support from family/friends 
Pelvic floor, general restrengthening of core (not for aesthetics, but for actual strength, stability, to alleviate back pain, etc), lactation
Mental health support would be the biggest item, lactation support, doula services (meals and baby tips), additional postpartum visits with ob midwives 
Home visits, postpartum therapy sessions, maternity leave for 6mo-1 year, at home lactation support
Emotional, lactation, pelvic floor,
In home visits 
Help navigating early weeks, postpartum doula, mental health support, help cooking and cleaning 
postpartum doula, in-home midwifery services, chiropractor, pelvic floor PT, acupuncture, meal train, paid leave
Meal train, massage, location, help with chores
Parent groups, emotional support, therapy to manage the transition to Parenthood stress, help around the home with cleaning and other tasks
Therapy, lactation support - including pumping!!!, nighttime support early on
Lactation-longer time off work, pelvic floor rehab
More time off with baby, check-in beyond 6 weeks with OBGYN, insurance coverage for postpartum visits with therapist, etc. 
Pelvic floor therapy, lactation consultants beyond those at the hospital, therapy, parent groups 
Lactation consultant, postpartum doula, night nurse
Lactation, pelvic floor therapy, chiro, mental health, counseling
 
Household help, lactation, emotional support or counseling, or pelvic floor physical therapy, reasonable maternity leave from work
Lactation support, talk therapy, pelvic floor physical therapy
Counseling, lactation, some sort of support group
Mental health, more health checks, in home support with food prep, cleaning 
Physical and emotional therapy/support. More comprehensive/longer support from OB. Postpartum doula support. 
Pelvic floor therapy, in home well check, lactation service, meal/home help, nighttime doula for sleep
Lactation support, mental health, body work, home derives, meal train, doula, nanny 
Postpartum doula
Food service
IBCLC
Support groups 
Home visits 
Therapy/child care/nighttime Douala/lactation
Lactation, meal prep, cleaning, longer paid leave
 in home check up, Therapy, lactation services
More paid time off 
Lactation
Maternity and paternity leave 
Infant sleep consultation 
Mental health support/check-in 
Mental health, lactation , meal prep
Physical therapy, a nighttime doula, and a postpartum mental health specialist 
House help, im home visits, longer maternity leave, better follow up medical visits
Paid leave. Pelvic floor pt, post partum counseling 
In home support, especially night
Help with housekeeping, care for baby while I rested and healed 
Breastfeeding, doula at hospital and overnight care at home so I could rest 
Lactation, pelvic floor PT, mental health therapist and psychiatrist, sleep consultant, nutritionist, child care, house cleaning, food supply, formula coverage, social work for other children, diapers
Meal support for at least a few nights a week for the first few months, pelvic floor pt, overnight doula help, hoise cleaning, occasional childcare, in home bodywork, paid leave for the first year, paternal leave of at least six months, education on normal infant sleep
Emotional support 
Emotional, lactation, 1st child care, financial and mental from work
Massage/chiro, in home wellness services
Someone to help watch the kids to get a break, and help cleaning 
More than just the 6 week appointment, counseling, meal train, housekeeping services, longer maternity leave, paid maternity leave, being more prepared for what to expect after birth 
Everything possible. 
Housework, cooking, emotional support. More time off work 
6-12mo paid leave, affordable childcare, affordable groceries/cost of living, LC support, PFPT, maternal mental health care/access to therapy, home visitors to check on these topics, meals
In home help, lactation, pelvic floor, emotional support 
Pelvic floor therapy, lactation, OBs who listen and not send you on your way after the 6 week check up, a year of talk therapy, mom groups
Longer paid maternity and paternity leave, lactation support, in home check ups postpatrum, earlier check up with OB postpartum (earlier than 6 weeks), access to laundry/food/home care services or financial assistance for said services, greater access to mental health care/screenings. And the flexibility to access these services not just in the weeks after birth, but over the course of the first year. 
Doula, lactation consultant, mental health, massage , pelvic floor pt 
Massage therapy, pelvic floor therapist, night doola, house cleaner, meal trains, mom support groups 
A 24/7 baby nurse
Anything to help with traumatic births, mental support, physical for my body and babies. Meals, household help 
Less expensive child care and longer paid leave
Postpartum follow up appointment, In-home help with tasks like laundry, cooking, cleaning, and child care,  Pelvic floor rehabilitation, massage or chiropractic, lactation support and emotional support 
In house pelvic floor therapy, being given extra postpartum supplies, being given extra baby supplies, extended maternity leave of at least one year
Meals, phone calls regularly answering questions
Lactation support but IN home!! (Not outside groups which were hard to attend), pelvic floor therapy, body work, post-partum doula services. 
Household chores, in home lactation, comprehensive postpartum follow up
Pelvic floor/strengthening help, breastfeeding help, education on tongue ties/lip ties and how they can affect feeding, easier access to postpartum mental health providers. 
Lactation, regular in home nurse visits
Pelvic floor, emotional, physical, home chores, childcare 
Lactation support, childcare support with other children, mental support, household support, disability for self employed 
Paid parental leave, affordable childcare, postpartum doula, lactation consultant, therapy
Pelvic floor !! All the Physical therapy possible! 
In home lactation, meals cooked
Home care. Chores. Lactation. Physical th wrapt. Massage therapy. 
Lactation. Pelvic floor. Emotional/mental health. Physical therapy. 
Meals, child care, trauma counseling, anything is better than Georgia offers.
Lactation support groups, in home lactation support
All of the support you listed in survey above
Lactation, wellness, meal train, household help
Longer maternity leave (6 months +), more than two visits with my doctor regarding recovery (would have loved help with understanding how I could exercise again without hurting myself post c section), additional help caring for the baby, additional help with chores around the house, in home postpartum visits, in home doctor’s visits for the baby. Look up what Germany does postpartum — I want that. 
- Affordable Mental/Emotional Support
- Pelvic Floor Therapy 
- Physical Therapy—my abs and back have never been the same after 3 c-sections!!
- Help with meals, childcare, house work
- Unlimited access to lactation consultant 
- Nutrition and fitness coaching 
- Pediatric helpline to answer questions about babys health & wellness
Im home follow up care, lactation consult, parent groups, physical therapy, mental health support, house cleaning
Mental health, better maternity leave
Occasional childcare, night Douala, meal train, mental health checks for me, in-home postpartum checks, longer parental leave for my husband. 
Postpartum doula, meal assistance, housekeeping, babysitter for older kids, pelvic floor PT, close friends, lactation consult, sleep consult, therapy, play groups 
In-home supports, parenting groups, family/friend visits, community play groups, certified/vetted childcare in-home, longer leave from work
Post partum depression counseling, emotional support, lactation services, help around the house, meal service 
Lactation. Home visits. Transition back to work emotional support 
Lactation 
New parent join 
PT
Someone to make me food 
House cleaner 
Real lactation services in person. Birth trauma therapy not just offering a prescription. Bodyworker. 
All that I had, but more often. 
Pelvic floor therapy, mental health support, lactation assistance, physical conditioning
Postpartum doula, mental health support/therapy for traumatic birth  offered immediately (took me long time to realize I needed it and even longer to get it), much stronger lactation support, more education on what 4th trimester would actually be like (not sugar coated), more help around house so I could rest and enjoy baby. 
I would want everything, being a new mom is so hard. 
Lactation, housekeeping, counselor, pelvic floor rehabilitation, post c-section activity/exercise or physical therapy
Pelvic floor rehab, lactation support for regular clogged ducts
In home care, in home baby assistance, household tasks, grocery/meals 
Postpartum doula, lactation support, pelvic floor therapy, postpartum social group, extended maternity/paternity leave 
Mental health, pelvic floor, lactation, meals/cleaning 
Meal train, paid time off for extended period, pelvic floor, massages 
More pelvic floor attention. 
Mental health support, meal support, household support 
Lactation support, paid parental leave greater than 12 weeks (6 months or more) for all parents, therapy, in home cleaning and laundry devices, affordable high quality childcare, supportive workplaces with universal accommodations for new parents regardless of gender or parenting role
Lactation, pelvic floor therapy, meals, house cleaning 
Everything in your list of possible support looks wonderful lovely and important.
Lactation to be covered by insurance.  A support phone number for mother's, like a 988 for a new mom.
Pelvic floor care.  I didn’t go for several years due to cost. 
Free lactation support, free therapy, free physical therapy 
Pelvic floor therapy, doula, nutrition/meal delivery, lactation, couples counseling, paid family leave, wellness visits for birth parent and baby, counseling
In home support, childcare, therapy, lactation support, pelvic floor therapy, nutritionist, mothers groups…
Physical therapy, more than one postpartum visit, counseling, in home cleaning and cooking, night nurse
Lactation support, meals, household help, sleep training, overnight doula, in-home postpartum checkups for mom and baby, new parent support groups, PAID LEAVE
Pelvic floor PT, childcare, community group 
Pelvic floor therapy, emotional support, medical visits, in home help with basic tasks 
Doula, help w laundry & food, massage, pelvic PT, psychotherapy, more OBGYN a visits to assess healing, lactation support, house cleaning, support for my partner
Mental health, first time mother support/guidance, respite service in the early weeks
Medical care for mother and child more often, helping around the house, emotional support, new parent groups, and mental health servicez
Massage/chiropractic care, community support
Extended family leave, pelvic floor rehab, massage,in home help, lactation
Lactation and pelvic floor PT in the home within first 2 weeks, pelvic PT ongoing through first few months. Postpartum counselor/psychologist. Postpartum doula to assist with baby tasks in the home and teach stuff. Meetup group with other moms every few weeks for socialization. Massage and chiropractic every month. 
Help managing the house, emotional support, trauma and grief counseling, food prep
Therapy, pelvic floor pt, childcare services, longer paid time off , lactation support 
Paid parental leave, In-home wellness visits from a nurse for baby and birthing parent, therapy, new parent groups, cleaning services, universal subsidized childcare
Night nurse, doula to provide extra care immediately postpartum so I could rest, cooking and cleaning help, pelvic floor therapy, lactation consultants, new parent group 
More paternal leave, more meal trains 
Nourishing food, childcare, emotional support 
Nighttime help in newborn phase. Pelvic floor therapy. In home Lactation support. In person support/“play” groups. Better information of possible complications 
Housekeeping, mental health/therapy, moms groups/respite care.
Household help, meals, cleaning 
Group therapy for PPD/PPA, in home wellness checks, massage. PT
In-home help with tasks like laundry, cooking, cleaning, and child care, emotional support, new parent support group, instant lactation access and understanding formula rather pushing for BF. Therapy for new parents and couples 
Pelvic floor rehab, nutritionist, lactation specialist, mental Health therapist, mom friends
Doula, therapy, in-house cleaning/cooking/laundry, MATERNITY and PATERNITY LEAVE that lasts longer than 3 months 
Best case scenario where services would be covered by insurance would be:
1. Lactation Support 
2. Pelvic Floor Therapy 
3. Postpartum doula (services to be used w/in 1st year)
4. Mental health services/therapy
5. Tongue tie services for the baby
Help at home, lactation support, body work, time off work, newborn education 
Lactation consultant, pelvic/abdomen check up, Obgyn follow up, emotional support 
What I stated above, lactation help, pelvic floor physical therapy, maybe weekly/monthly check-ins with a professional about how baby is doing  and to answer questions because esp as a first time parent I just don't know what to expect
Emotional support, meal prep, physical support, help with other children
In home nurse check multiple times, longer paid time off work, online follow up programs to assess emotional state, screen for post party depression 
Longer paid leave, in-home lactation support (multiple visits), household help (cooking, cleaning, childcare), in home well baby visits
I would’ve benefited more from services that weren’t provided. Better information and access to post partum therapy/groups. Lactation consultant covered by insurance. Employer Paid recovery leave for at least six weeks. 
Automatic pelvic floor consult, mental health support, home visit from doctor, night nurse for first few weeks, food delivery, house cleaning service 
More paid time off for my partner (got 4 weeks), would have loved at least 12; better mom-to-mom connection (limited bc of Covid)
Latation, mental health, night nurse, meal train, house cleaner, nutritist, 
Longer maternity leave 
Access to mental health services quickly and affordable, in home postpartum doula, lactation visits etc etc
Therapy, childcare, pelvic floor work, lactation support, meal service, care for older children 
Nicu-specific therapy and group therapy, pelvic therapy and physical therapy for C-section rehab, pediatrician that isn't overloaded and can dedicate time to you and your questions
Lactation support, pre-birth emotional preparation for both myself and spouse. More frequent OB visit. Pelvic floor rehab as standard. In-home nurse visits for baby instead of in-office Dr visit. More paid leave time for myself and spouse. Support for spouse taking time to be home and adjust. Mother/baby classes as standard. Sleep/care classes or respite stay. 
Longer maternity leave, affordable and reliable child care, lactation referral at the time of hospital discharge
Pelvic floor rehabilitation, check ups with OBGYN, emotional support from a psychologist/therapist, lactation support AND formula education/support 
Midwife check and ibclc visit at home in the first week after birth, a postpartum checkup in office sooner than 6 weeks and another check after 6 weeks (one checkup just isn’t enough!), pelvic floor physical therapy, night nurse for early days, help with other children during the day from family/friends 
Longer paid leave, paid counseling, more personal follow-up appointments other than 6 week appointment.
PP doula 
More proactive check-ins from doctors for maternal care. 
I’m home services 
All that were listed above. Still have never received pelvic floor rehab. 
At home visits from professionals, especially mental health so you don’t have to try and assess yourself
Household chores support, childcare, emotional/mental health, lactation, new parent education AFTER birth, grief counseling and support groups for medically complex baby in NICU, help navigating state Medicaid and other systems for child with disabilities
Night support, lactation, meal prep, housecleaning, wellness/counseling, mom groups
Postpartum doula, lactation, mental health
Lactation counseling as standard and easily accessible, in home help (hold the baby, laundry, meals, whatever it takes so mom can sleep) more paid leave from work for BOTH parents (this would help with sleep for both parents), support groups for moms specifically.
Babysitting, lactation assistance,  pelvic floor rehab, psychological counseling 
Longer paid parental leave, lactation, mental health support, postpartum doula, mom/baby groups 
Lactation consultant, night nurse, help with food prep, cleaning, nanny/childcare, 6 months paid maternity leave, pelvic floor or massage 
In home help with tasks, body work, full blood work panel (without having to make an appt and ask for it)
Emotional support, wellness checks, longer parental leave, easier access to childcare when returning to work, more affordable childcare, flexibility in returning to work (instead of being on leave and going back 100% of the time, easing in 50%, then 75%, then back to full-time), automatically prescribed pelvic floor therapy, resources for C-section scar recovery, more accessible parenting classes to provide information about the reality of the first year postpartum
Help with childcare, physical/mental/emotional load, lactation support, therapy, therapeutic massages, pelvic floor therapy
Virtual / video appointments for therapy or assessments (which weren’t offered then but are now), affordable and high quality childcare, night nurse/baby caregiver, house cleaner 
Pelvic floor assessments, mental health assessments, massage, in home assistance, parenting groups/classes, virtual options 
Lactation, pelvic floor, counseling - also more education surrounding options, not just a packet of info
Child care, physical therapy, mental health care, postpartum physical recovery, paid parental leave for both myself and my spouse, support groups
Postpartum doula, Lactation support, food, childcare, maternity leave
I think more postpartum check ups would be beneficial. Every mom should get at least one appt with a lactation consultant even if it is to discuss pumping etc. It would be great if i hadn’t needed to create a mom group but if those things were already in place and easily accessible for everyone. It would be great if part of your postpartum care included some therapy sessions since motherhood changes and shifts everything in your life. I have a supportive spouse but wow the difference it made when he had paternity leave. With our first he didn’t and could only take a week off with our second he had leave and had 5 weeks off. That made a difference in my mental health because I had help for longer in the beginning with sleep and daily tasks because he could be there to help. 
More household help and counseling/therapy 
sleep support, lactation support, cooking/nutrition support for self and family, home cleaning support, mental health support, physical healing support 
Nanny cleaning help lactation consultant post pattume doula
Pelvic floor rehab, help around the home in home postpartum/newborn follow up 
Checkups and check-ins more than once or twice with a midwife or ob-gyn. Mental health screening from an actual mental health provider. Pelvic floor physical therapy. Lactation support that's actually unbiased. A postpartum doula or night nurse. A meal train or similar service. In-home help from friends and family with everyday chores so that I could rest. 
Monthly mental health appointments, therapy, massage, night nurse, pelvic floor physical therapy, personal trainer, nutritionist 
Paid time off, lactation support, paternal mental health, night nanny/doula. 
General health and wellness, mental health and transition, pelvic floor PT, and lactation consulting 
Pelvic floor PT, lactation/ feeding support, household support 
In home care for baby and me, automatic enrollment in mom support group, required postpartum mental health therapy, recommended marital counseling
I wish I had known about pelvic floor therapy. Was not really a thing. I knew about the Tuppler technique and the exercises in the books.  Had to see urologist for leaking. 

Housecleaning
IBCLC
PT/Pelvic Floor Therapy
Laundry help
Someone to help with other kids (nanny, family)
Massages
A cook! Ha!
Sleep sleep sleep. Help with sleep training. Help with the baby to let me sleep. She was colicky and often slept in 15 minute increments. I was so sleep deprived I thought my heart might stop. I also would've loved to have been a part of a new mom group, a meal train, pelvic floor rehab - basically everything you listed would've helped - I felt like I was lacking in everything
Pelvic floor therapy, counseling, house cleaning, peer therapy sessions, lactation consultation prior to delivery 
In home lactation support, post birth doula, mental health support 
Night nurse or sleep training consultant, postpartum depression counseling, more paid time off or subsidized childcare 
Lactation support, in person mom groups, pelvic floor therapy, some kind of check in other than from the pediatrician office would have been great. Help at home would be a dream.
Emotional, pelvic floor, therapy 
Night nurse!!, post partum mental health support (just a general check in), lactation, child care
Cooking, cleaning, location OR formula, pelvic floor PT, massive/acupuncture, support groups
Lactation support, wellness, mental health, pelvic floor
Lactation consultant, the postpartum care to match the prenatal and the pediatrician looking out for mom’s welfare. 
mental health - learning how to ask for help while struggling emotionally 
Weekly therapist, in home well check for me and baby following my c sections, in home child/mom sleep and lactation support.
Lactation support, childcare, mental health care, nutritional health
Mental health, lactation, meals
In home services, therapy, more frequent medical appointments, low cost chore/meal service 
Paid Maternity leave, breast feeding support, childcare support, nutritionist, therapist, physical trainer, formula support
In-person Lactation support par least two the first thr month and one every month until month 3
Meal services /cooking 
Housekeeping 
Midwife check ups, lactation, pelvic floor pt, help with meals
Post birth counseling/ therapy, pelvic floor/postpartum physical therapy, lactation support, in person mom groups, family to help or for hired help at home, night nurse some nights 
Paid maternity leave of 20 weeks minimum for both parents. All women be referred to Pelvic Floor Therapists postpartum like in France at 6-8 weeks postpartum. Help getting parents sleep when they need support. Automatic contact/follow ups with lactation consultants. Home visits for those early newborn visits—it’s so hard to get out of the house for those the first month. Waived delivery charges for groceries and food the first month. Automatic therapist/counselor virtual visit offered for postpartum mental health screening, more than once throughout the first year. 
Physical support for healing from C-section over the whole year. Childcare, in person groups. 
Lactation support, more than one postpartum visit, counseling visits, pain meds BEFORE iud insertion, 12 + weeks paid maternity leave, cheaper childcare, Doula, pelvic floor PT, chiropractor care, in-home care, and massages. 
Paid parental leave, mental health coverage for insurance, dedicated counselors for NICU families at the hospital, more than one postpartum OB visit, easy access to lactation support, meal train but with gift cards for convenience when in the NICU, in depth car seat safety education
Physical therapy/rehab, therapy, acupuncture lactation support, postpartum doula, childcare access
Ensuring proper nutrition for myself. Some sort of person to help teach me instead of going trial by fire, any sort of house work help. Maternity leave longer than 5 days, proper child care and support when making that decision.
Feeding support, emotional support, trauma counseling, pelvic rehab, child care for older sibling, more time off for partner.
Childcare, laundry, counseling, medical
Lactation support. Emotional support. Better post partum physical care 
Lactation, pelvic floor PT, meal prep assistance, doula, nanny, cleaning assistance, counseling 
Lactation, night doula, post partum doula, meal service, childcare service to get breaks early and often, psychiatrist and therapy for PPA / PPD, parent coaching, exercise coach 
Lactation, therapist/mental help, additional OB follow-ups for those who want/need them 
I needed a night nurse, someone to check me as often as my baby was getting checkups, pelvic floor therapy, paid maternity leave, help with childcare, a cook, a house cleaner.
Mental health, physical rehab/pelvic floor, postpartum doula, parent group, household task support, IN HOME lactation and wellness visits
Mental health support, pelvic floor,  massage and chiropractor for back pain and household help.
Any and all. We don't have a village being from out of state.
Lactation support, depression/stress support, Infant sleep, Financial resource education, Support with family leave laws, Education on how to navigate post partum body
Someone to come in and help with household tasks like dishes, mopping, vacuuming, lactation appointments in the first few weeks scheduled so you can get help if needed, pelvic pt for everyone, 
Meals, household help, pelvic pt, 
Way more checkups from obgyn, counseling to manage new emotions, free lactation consultations, support group for 0ostpartum anxiety
More mental health support. Therapy, places that could help when questions came up, somewhere to go for support if you weren’t given it. 
Pelvic floor therapy, mental health therapy, more than one check up after birth, home help (cleaning, cooking, etc.), maternity/paternity leave (paid). 
Lactation support, massage, parent groups, therapy, night nurse, house help
Someone to come to the house and check on us and baby, help with laundry and cooking meals, parent groups, more paid time off for partners, pelvic floor therapy, lactation consultant, more follow ups with obgyn, advocate at pediatric appointments, more sleep!
Child care, pelvic floor therapy, mental health services, meals, mama support groups 
Access to sleep training courses, baby led weaning courses, pelvic floor therapy, help cleaning the house and cooking on a regular basis, someone to watch the baby for two hours so I could connect with my partner. 
Emotional, child care l, household help
Pelvic PT, counseling, childcare
Lactation consultant, pelvic floor PT, postpartum doula, mental health therapist, meal train, in home support/help
All of them!
Help with household tasks, childcare, food. 
Better maternal & paternal coverage, nurse visit at home , breastfeeding help, pumping help, more practical pumping plan with work.
Lactation, emotional, new parent groups, pelvic floor care, meal train/cooking/cleaning
Chiro, pelvic floor, share group, in home checkups
In home childcare, required mental health checks with postpartum visits and follow-up care beyond the regular 6 weeks check-up.
Post partum education, resources for PPA/PPD, counseling 
Mental health and well-being support, social connection with other new parents, massage and/or other maternal physical care, medical coverage and monitoring, judgment free infant feeding support, affordable childcare, child development education, birth control/family planning support 
Massage, night nurse, therapist, medical, lactation, meals
In-home pediatrician and OBGYN visits. Leaving the house in the early days was so hard.
Counselor/psychotherapist; lactation support; laundry, cleaning and cooking assist; Physical Therapy; OBGYN post-partum checkups every 2 weeks for the first 6 weeks.
A home visit to check in, problem solving, sharing resources, motivating and helping me find ways to exercise for physical and emotional health. Small support groups to meet others would be a lovely way to build engagement and connection. Meals and nutrition be if teaching, sharing ideas/resources, or providing a set amount of time. 
Mental health- PPD/A, housework, childcare, meals, therapy
Household help- someone to help with laundry, cooking, cleaning etc. A sleep specialist to help learn about baby sleep. Post partum counseling (and childcare for the time you spend there). Pelvic floor PT. 
- how to care for my body, mind, spirit in first year
- childcare 
- home help so I could rest/sleep to make up lack of sleep 
- someone to talk to to be able to process experience 
Pelvic floor rehab, bodywork, housekeeping/meal assistance, home visits via nursing to ensure safety and proper medical recovery, laceration, counseling, 
Postpartum check ups to make sure I’m healing correctly, pelvic floor or outpatient PT to address all the MsKL issues from pregnancy and birth, lactation support, new mom/parent groups, in house support and couples/marriage counseling would be amazing bc everyone has the same struggles and doesn’t talk about it
Parenting group, emotional support (therapy or something similar), support going back to work (or more time on leave)
Postpartum doula, PT, lactation, massage, in home help
Automatic lactation support, enrolled in a cohort mom group, and pelvic floor physical therapy 
Night nurse, lactation support, therapy, pelvic floor therapy, childcare 
Lactation, therapist, frequent in home follow ups from healthcare provider, massage, family help, help from friends, household help
Pelvic floor rehab right away that is covered as preventive care (free), postpartum doula to help with house hold chores and the baby, in home lactation support, anxiety support, overnight baby support so you can sleep!, healthy meal delivery, better insurance coverage for breast pumps that don’t require you to stay attached to a wall or carry a large pump around. Longer maternity leave to actually recover and feel ready to go back to work. Financial support while on maternity leave. In home baby visits instead of going to the pediatrician office…have them come to the house. New mom groups covered by insurance! These groups are so important.
Pelvic floor rehabilitation, lactation consultant, 
Therapy. In home care or a postpartum doula.
Lactation, postpartum doula, massage, physical therapy, meals
Mom groups through hospital or doctor office. More breast feeding support. More info about postpartum mental health changes. 
Doula, Lactation consultant, mental health support for mom 
Community support, postpartum doula, maternal care focus
Compassionate lactation support, mental health support, physical therapy, parental support groups/ community building, and in-home wellness follow-ups in the immediate weeks following delivery/hospital discharge after dealing with an emergency Cesarean (because getting in & out of the car to get to those appointments was painful!)
Postpartum doula, in home assistance for activities of daily living, lactation support, pelvic floor PT, mental health services 
Emotional support, parent education, household help (cleaning, cooking), in home personal care (haircuts, massages), in home lactation support, pelvic floor rehab 
Childcare and therapy 
In home help, more paid leave
Overnight help or house cleaning/meals
Laundry, housekeeping, time to sleep more
Lactation support, postpartum doula, cleaning and meal assistance, affordable counseling to address PPA
More physical support to take care of the baby, myself, and my home. This would help my mental health. I didn’t specifically need it, but I think pelvic floor therapy should become the norm. My bladder control was a little wobbly for a few weeks. 
Pelvic floor therapists, more lactation support, ongoing therapy, more postpartum follow ups with obgyn or midwife. 
In home assistance - night nurse would have been a dream. Also lactation consultant after 4 weeks - my second had issues nursing that developed in month 3 and I couldn't find a lactation support for past the newborn phase. Extended maternity leave. Nutrition support - after my first, I became malnourished trying to diet and continue nursing. Didn't know I shouldn't have done that. Also endocrine screenings because everyone attributed my exhaustion to new mom and it wasn't until years post partum that anyone considered my thyroid could be an issue or that my struggle with baby weight might be insulin resistance because I had none of these issues before pregnancy.
Therapy, PT, longer paid mat leave to fit in all these appts ! 
Postpartum Depression care; better lactation support; pelvic floor rehabilitation 
In home help, pelvic pt, pp therapist, sleep consultant, in home lactation support, tongue-lip tie eval and treatment, paid maternity leave
Mental health, lactation, massage, chiro
Chiropractic care for baby and mom
Lactation support 
Meal train the first few weeks postpartum 
In home help to clean and do laundry
A night nurse, baby sleep consultant, sibling care, meal trains, support for colicky babies all of the things listed above. 
Emotional therapy, domestic help, overnight baby care, body work
Regular health care check ups, postpartum doula support, in-home visits, mental health visits, new parent support groups, marriage counseling, pelvic floor rehabilitation. TIME just to heal and recover.
All from your list! Especially in home help with chores and meals, lactation consult, wellness support, additional postpartum visits 
Doula, more postpartum visits, therapist, in home care for the first week or so at home with new baby, night nurse for baby
Meals, night nurse, lactation support, household tasks, laundry, pelvic floor PT, therapy 
Mental health, household help, night doula once a week for better sleep
Lactation consultant with regular follow up, massage therapy and chiropractic, housework/meal help, postpartum doula
Lactation, counseling, pelvic floor, increased OBGYN follow ups; in home infant wellness checks at 2 days and at 2 weeks 
Lactation consultant, babysitter, therapist.
Lactation, mental health, physical therapy
Counseling/emotional/mental, pelvic floor, lactation support, household help/food 
More appointments with my OB postpartum. 
Night nurse,  better depression screening,  house keeping,  early intervention pelvic floor rehab
Lactation support, mental health care, household support, pelvic floor therapy, new parent groups
Therapy immediately, pelvic floor therapy, massages, support groups, lactation
Pelvic floor therapy
Lactation support
Mental health/social well being check ins
Managing postpartum anxiety 
Sleep support 
I think women should AUTOMATICALLY be referred to a pelvic floor PT specialist following a birth. I didn’t have noticeable issues until 2 years after birth (so I didn’t seek help until then), but they said it would have been better if I went soon after birth. 
Pelvic floor, therapist, sleep consultant 
I think this country needs to either provide more adequate maternity and paternity leave or it needs to be providing in-home supports. I think mental health care support would be extremely helpful. I suffered from severe postpartum anxiety, and that played a significant impact in my life. I think new mothers could use help with everything from emotional care to household maintenance to support in the financial costs of adding another person into the budget. 
Pelvic floor PT, in home support (cooking, cleaning), medical postpartum follow-ups (MORE THAN 1!), lactation consultants, postpartum doula, childcare
I would have loved to have a postpartum doula to assist with care for me, especially after my first (preterm delivery, preeclampsia, long NICU stay, significant tearing for me). Other types of support I would want: household help to allow for more bonding time, lactation support (I cobbled it together from reading Internet forums), pelvic floor therapy much sooner, meals, a longer (paid) maternity leave, the opportunity for my husband to have paternity leave (he had zero with either child), more support upon returning to work from my employer, trauma therapy to assist me in processing my first birth in a healthier way. 
New parents group, therapist, physical therapist, lactation consultant, meal train, house help to keep up with some basic household chores, 
In home postpartum follow up with a doula, in home lactation support, pelvic floor therapy, more follow up and care beyond 6 week checkup 
Paid parental leave for significantly longer for myself , any paid parental leave for my partner, help with basic household things like cooking, cleaning, grocery shopping, laundry, lactation support, new parent emotional support, childcare 
Household cleaning, food prep, childcare, mental health, fitness, lactation, solids transition, more than 1 postpartum medical follow up. 
Child care, meal program, postpartum appointments and check ins, grief support
Time for self care, more maternity time to bond with my baby, help with other children, assistance with household tasks
Paid family leave, pelvic floor care, lactation services, post maternal care (mental & physical), support groups or therapist, childcare. 
More time off, housecare & in home help, lactation, massage, meals, counseling/check ins, more medical check ins for baby and me, paternity help/checks/emotional, hotline for medical/care questions
Childcare, meal train, help with housework, my partner home for a month to help, paid time off to spend with my child
Doula, therapist, lactation, physio, massage, in-home help (cleaning and meals)
Emotional,  physical, in-home 
Therapist, emotional, financially cover more (insurance), chiro and massage, support person for breaks, 
Everything listed in the questions above!
As many as possible of all the service offerings you listed above would have been amazing. I could have used help re-strengthening pelvic floor, abdominal, & leg muscles, particularly after deliveries 2&3. I experienced patella dislocation after pregnancy #2 and (more severely) #3
Psychologist, pelvic floor physical therapist, family members during the first months, lactation consultant 
In home help, childcare, wellness help, emotional help, follow up help, meal service, new parents groups,
PAID FAMILY LEAVE FOR ALL. Help with household chores, laundry cleaning, prepared meals. Care for baby when showering, getting a nap, or periodically at night. Pelvic floor physical therapy. Support group led by postpartum doulas. Lactation consultations, in-home support and education for breastfeeding.  
Mental health, massage, pelvic floor rehab, chiropractic, childcare, lactation support, community and family support, nutrition support
Lactation support, help with nutrition, mental well checks more than just checking off items on a list on a piece of paper. Doula support at home postpartum. 
Everything listed above
Housekeeping, dog walking, laundry, cooking, couples counseling
Mental health, postpartum body care, home care tasks 
More emotional support. 
Pelvic floor, more lactation help, in home help, night doula
PP support group, more PP visits with providers and not just 6 weeks, pelvic floor assessment and PT if needed, lactation visits, easy access to mental health services 
Emotional help, more of what to expect when you go home from hospital. More help with the pain of breastfeeding and managing it with daily life, more breaks, more sleep. better follow ups from doctors! 
In home care for parents and baby, meals, mental and emotional support, food, formula, diapers, wipes, massage, rehabilitation 
Mental health support, pelvic floor therapy, help with cleaning and food, night nanny occasionally (for sleep), emotional support, cesarean scar mobilization, socialization during leave, longer maternity leave
Lactation, financial, mental health, groups 
Lactation, meal train, emotional support, family support, financial support, therapy
Weekly visits from a midwife/support professional for first two months after birth. Physical therapy for rehabilitation. Ongoing lactation support. Parent group with folks who had babies around the same time, with babies at group. Moms/caregiver group for emotional processing.
Therapist, cleaning/household support, acupuncture/wellness specialist 
Doula, live-in family members, spouse, close friends, childcare 
Pelvic floor Pt, more Ob visits (I had a 4th degree tear and it took months to heal), easy to access lactation consultant, therapy, meal support, emotional support, babysitter/helper, house cleaner
Lactation support, postpartum counseling, breastfeeding assistance and coaching. 
Mental health, pelvic floor PT, lactation support, in-home postpartum checks, more postpartum visits, meal trains, new parent groups.
Meal train, housekeeping, emotional/mental health, pelvic floor PT, paid parental leave. 
Pelvic floor PT (and child care for the PT sessions), meals brought or cooked, house cleaner, therapy, lactation consultant, baby nurse to help guide and provide child care, time to work out
In-person lactation support, pelvic floor PT, chiropractic adjustments and massage, and night nurse for newborn sleep support
Extended parental leave, pelvic floor pt, cleaning services, dog walking, dad groups for stay at home dads
Emotional support, someone to ask questions to, lactation consultant.
Postpartum doula to help with nursing/recovery, night doula to allow for sleeping, in-home visits from a nurse/doctor, pelvic rehabilitation, overall wellness guidance (dealing with lack of sleep, back aches from nursing, etc), individual counseling, family/couples counseling, video advice calls with pediatrics office, meal services, new parent classes, baby safety resources
Additional medical follow up appointments, included mental health appointments
Childcare, home cleaning,
Housework, meals, physical recovery
Postpartum medical check ups, postpartum nurse nurse midwife, postpartum doula, meal train, emotional support, pelvic rehab care
All of them above and it still didn't feel like enough. I might be getting diagnosed with OCD or ADHD tho.
Childcare, longer paid leave, housecleaning/meals, therapy, social support
All of those listed above. Truly - all of them. I wish we had friends and family who would have made us a meal train, but we didn’t. I wish we had providers who could come into your home to do check ups and help. We didn’t except for the expensive doula we paid for. 
Lactation support, meal train, emotional support 
Lactation support & someone to check in on the mental health of the mother, particularly after the first baby 
Therapy, psychological support. In home care services, health checks for mom and baby and household support/meals. 
Pelvic floor therapy, emotional therapy, and nutrition and physical coaching, affordable and available childcare 
Longer maternity & paternity leave policies (minimum 6 months)  Postpartum doula, night time doula / nanny, pelvic floor therapy, at home wellness appointments, way more follow up appointments than just 1 at six weeks, IBCLC,, in home help with meals and cleaning, therapy, , spouses learning more about “Fair Play” (by Eve Rodsky), new parent support groups (more online group support during Covid), acupuncture, more support from society in risk mitigation during a pandemic with babies / toddlers. More accessible, AFFORDABLE (subsidized) day care options for everyone who has to return to work (currently 1 year wait lists for best programs locally),  subsidized nanny care if possible, better support at work & better wellness rooms for pumping, flexible work schedules, Government & businesses need to prioritize supporting parents (she/her, he/him, they/them). Adopt similar support like Denmark & the Scandinavian countries. 
Night nurse, meal train 
Home visits from a nurse, lactation consultant, pelvic floor physio, community centers for new parents, maternity leave... at least a year off work
Emotional support, lactation support, pelvic floor and general PT, parenting education, in home support (meals, cleaning, etc) 
Meals, cleaning, pumping, feedings 
All of the above- family support, doula, psychiatrist and therapist PLUS meaningful multiple obgyn visits to check my healing (second degree test) instead of a cursory look once at six weeks. Pelvic floor therapy as a standard medical visit instead of an insurance hassle. I had /have bladder prolapse- basically my bladder was hanging out of my now slightly busted up vagina- after my second child … and have had zero care or follow up about it beyond “do some kegels”
In home help. Emotional support. Therapy. Lactation support. Meal service. Pelvic floor therapy. CHILD CARE. 
Meals dropped off, house cleaned, laundry done and folded and put away, someone take care of new baby so I can shower or eat or spend quality time with my spouse or other kids, pelvic floor therapy, I’m not sure what else but I’m sure there’s more (I just have new baby mom brain)
See above 
Self-care, laundry help, meal prep, lactation support readily available. 
PPD support groups, lactation help, therapy 
Therapy, in home tasks, postpartum doctor appointments, lactation appointments, pelvic floor therapy, meal services, massage therapy, postpartum night or day doula at the beginning, support groups/mom groups.
PPD and anxiety help
Pelvic floor PT, more frequent physician visits (one at 6 weeks was far too long), meal support immediately post parting, sleep consultant for baby, mental health counseling for both parents and as a couple, breastfeeding support that wasn’t “breast is best” only, tongue tie consultation and specialist for baby, new mom support group  that wasn’t focused on breastfeeding
Paid maternity leave, counseling or some kind, new parent classes, physical therapy for healthy recovery from c-section, emotional
Massage, therapy, housekeeping, cooking, moms group 
Pelvic floor PT, more frequent follow up with OBGYN, in home services (laundry, cooking, cleaning), more frequent and/or in home lactation consultant services. 
More medical checkups in first 6 weeks, routine mental health care, routine pelvic floor appointments
Lactation consultant. In home doula. 
Every OB GYN office needs a perinatal therapist on staff for their patients
Lactation that’s not just for nursing. PT. Emotional support that just happens-check ins. Real check ins not just one week later 
Housework, cooking, therapy, pelvic floor pt, 
Pelvic floor therapy, therapist
Postpartum f/u with OBGYN, postpartum doula, meal prep help, house cleaner, pelvic floor PT, chiro, therapy, lactation
IBLC, night nurse, cooking/cleaning, pelvic floor therapy
Anything and everything. I'm not sure I would have declined any support offered. It was so hard and disorienting.
Lactation consultant, personal chef, house cleaner, nanny
Night nurse
Breastfeeding/pumping support, weekly mommy group, pelvic floor therapy, family support, meal trains, mental health therapy, massage, chiropractic 
All the above 
Pelvic floor therapy! Postpartum anxiety therapy. Massages. 
Everything listed above in the question: What types of support did you have access to postpartum?
Lactation support, new parent group led by licensed therapist, pelvic floor PT, more regular Obgyn visits for first year, longer maternity leave (USA), couples therapy and individual therapy.
Therapy, parents group, doula, sleep consultant 
Postpartum doula
Therapy or counseling, pelvic floor rehab, additional obgyn appointments, laundry and meal services 
A postpartum health aide at home the first couple weeks (look into this program in the Netherlands, they provide that to new moms there) - to help with baby, house chores, sleep, etc
Psychiatry, therapy, night nurse, personal trainer, chef, cleaning service
Counseling, feeding (beyond breastfeeding support/include formula/bottle feeding info), more postpartum check ups for mom, pelvic floor therapy, cleaning/meals/in home support
Lactation, in home help with household tasks, new parent group in person, Dr checkup in person (mine was virtual!), meals, physical therapy/fitness for support strengthening my body again
Night nurse, postpartum doula, lactation consultant, pelvic floor PT, childcare, house cleaning, chef
Closer follow up care from my ob would have been great. My blood pressure was extremely high for two weeks postpartum and because it wasn’t accompanied by headache the doctors kept dismissing it. 

I needed major lactation support. I only kept at it because of the sheer intensity of hormones and my own stubbornness but also felt stuck with few options for help and was charged a huge bill for unhelpful lactation consulting. Eventually I found an IBCLC after a lot of searching in Facebook groups asking other people for help, and at 7.5 months got my baby nursing after exclusively pumping all that time. This was incredibly stressful and took literally months of my life (600 hours of pumping in 7 months). 

I would have absolutely loved any help at home. My baby was born in 2020 and so all dreams of hiring someone to help me went out the window. No one came into my house because of pandemic quarantine protocols. It was in some ways very special to have that time just me and baby, but also so, so difficult. I’m envious when I hear of the kinds of support that others get from friends and family. My friends did make a meal train for me and that was helpful for those first few weeks. 
Pelvic floor rehab, child care, in-home post Partum, in-home help, massage, emotional support
Longer Paid maternity leave, lactation support, affordable safe childcare, better health insurance, access and recommendations for pelvic floor rehab
Postpartum doula care. Nanny. In home visits from the community. Support so that I could sleep. 
Mental / emotional support., in home task support 
Lactation, pelvic floor therapy, mental health for PPD/PPA, diet and nutrition
Pelvic floor therapy, psychological assessment and therapy, support groups, in home postpartum care, food delivery, childcare for older children
Midwife, family support, rest supper for spouse and myself, overnight nurse/support, meal train, housekeeping, in person support group of other postpartum moms
Therapist. Psychiatrist. Night doula/help. Lactation consultant. Postpartum group. 
PT, lactation, sleep training assistance, emotional support, in home childcare 
Postpartum doula, postpartum mental health. Lactation consultant, pelvic pt
Pelvic floor education/support, targeted nutritious meals, housekeeping, mental/emotional support through therapy, in home lactation support, in home follow ups for first four to six months. 
1. In home lactation support, provided by insurance. It was excruciatingly painful to make trips back and forth to the hospital (30mins each way) for lactation and weight checks starting 3 days PP. With both babies we had weight gain issues and for the first month we would have to go 1-3x a week. (Kaiser Permanente insurance needs to make serious improvements in this area) 
2. Emotional well mama therapies/counseling with a postpartum therapist would have been extremely beneficial. My mental headspace was better with the 1-2 child change but maternal mental health is in my opinion in a very fragile state. Even with having community and family we need to provide dedicated support in this area. 
3. Legitimate meal train/home support. It’s a lot to put on ONE partner to have most of the cooking, cleaning, childcare (of older children), and attending to postpartum mom alone. Even when you have family close it’s hard. 
Lactation, in home check up after delivery for less disruption and movement after tearing,
Pelvic floor therapy 
Massage therapy, ongoing IBCLC visits for the first few months, chiropractic care, in-home cleaning services
Longer maternity leave, assistance to pay for day care, lactation support
IBCLC, postpartum doula 
Sleep training once age appropriate, more lactation support, post partum doulas, and mental health support. I had PPA and PPD and it was really horrible to deal with. 
In home help, lactation support, massage/chiropractor and Accupuncture 
Post partum doula, lactation consultant, pelvic floor PT, meal and laundry help, group music therapy or just meet ups with local moms and babies 
Overnight care, meal prep, lactation support, MORE paid and unpaid leave, therapy, new parent group meetings, sitters for older children
THERAPY!
Meals, counseling for both parents, post partum doula, lactation, pelvic floor, exercise 
In home support from a doula 
All of the above plus in person family support, childcare for toddler, everyone PP needs pelvic floor PT. 
Pelvic floor, therapy,  massage, chiro, lactation, help ij the house 
LC
Emotional. Talking me through the depression I went through. In house support or assistance with meals, cleaning or errands. Being able to sleep more would have helped a lot longer time off for my husband 
Postpartum doula, in home lactation consultant, chiropractic care, meal support
Paid time off of work for at least one year, especially during this period of breastfeeding. Pelvic floor therapy. Massage therapy. Some sort of way to ease back into exercising and child care during this. Lactation support. Assistance with cooking, cleaning, and break from watching baby to shower/sleep. Postpartum Dr visits. 
Meals, more PP follow up appointment, in home support to check on me and baby, pelvic floor assessment (standard) then therapy if needed, 1-2 years leave from work 
In- Home Lactation support, pelvic floor rehabilitation, in-home task assistance, massage, in-home wellness services, meal train 
Home visits for follow up appointments, lactation, etc. basically anything so I don’t have to leave the house
12 weeks paid leave, another 4 weeks optional leave, 5 weekly doula visits for 3 hrs each, doula services that were fsa eligible, rule in fsa that for expecting parents, you can change contribution limits mid-year, tax credits for childcare that costs more than 15% of income (currently spend 33% of pay on one child’s care, if I have a second, that will double). Two standard postpartum doctors appointments (standard is one apt at 6 weeks, would like 2 to be the standard and covered by insurance). 
mental health counseling, couples counseling, postpartum doula/ specialist 
More emphasis on recovery one six week appt really doesn’t cover it. Postpartum doula. 
I loved having cooked meals dropped off in those early weeks. Also lactation support; I still needed it even with 4 kids. Perhaps even an in-home appt for mental health… just once or twice to tell me “this is hard, this is normal, and you’re doing okay.” They (RN? MSW? Care Manager?) could refer mom to any services that seem appropriate.
Night nurse, lactation support, mental health support, pelvic floor, food, childcare for older child
Household, financial, emotional, physical, medical - basically help in every aspect 
Mental health therapy, pelvic floor therapy, in-home lactation consulting, exercise support/advising, parent support groups. 6 months paid leave minimum. 
Fully paid leave (not having to drain sick days / take unpaid time), all the care I listed above, in-home follow-up would be ideal
Cooking, cleaning, therapy, chiropractic, yoga, childcare assistance
It would have been nice to have massage and acupuncture, and other self-care measures ! Lots of good food, extra hands to help around the house and with emotional support, in-home medical care
I would have loved to have a nurse come the house to make sure everything was going okay. Support with household chores / someone to talk to while partner was gone. I had postpartum anxiety and support there other than medication would have been nice. 
Postpartum doula, meal services, house cleaner 
In house help, night nurse one night/week, counseling, lactation support
Night nanny, daytime nanny, family and neighbor support, new parent groups, c section scar care, a birth and pregnancy debrief, therapy
I’m home visits from a nurse, therapy
Home visits from nurse. Reliable childcare for older child. Someone to help with baby so I could sleep- possible night nurse. Help with meals and laundry
In home support and therapy 
Lactation, mental health or therapist
Lactation support from a specialist with knowledge because not all medical staff are versed well in this area and give bad advice. Parental support groups. 
All of the above plus actual maternity leave for longer. I took about 3 months of vacation/sick time that I saved up and was constantly called for a date to come back to work. I was breastfeeding had a preemie and was definitely not mentally or physically ready to return. 
Pelvic floor/c section therapy, in home wellness checks, mental health professional, and parenting coach for new parents.
Postpartum doula, postpartum therapist, lactation support, OBGYN visits, family assistance, pelvic floor therapy 
At home visits to check on mom and baby. Having to go to a doctors office three days post C-section is miserable. More mental health services for moms. That first baby really takes an emotional toll on you. More information about what is considered “normal”. Actually extended pay for families. 12 weeks of unpaid leave. Does nothing for our family. We need more maternity and paternity leave that is paid. More access to Dullas. Pre-birth. During birth. Post first.
Help around the house, childcare, massage, pelvic floor therapy, postpartum depression therapy, baby care classes
More postpartum check ups 
In house help, mental health support, meals, massage, dog walking/pet care 
Lactation support, overnight support,  PP doulas, more appts with OB and earlier than 6 weeks PP
Help with learning how to take care of a baby. Especially sleeping (how to form good habits). Dealing with my own ppa and ppd. Not recognizing it when it happened
Therapy, more than one follow up visit, Chiro, in home visits. 
Birth doula, postpartum doula, pelvic floor therapy, meal train, mass freezer meal prep for families with severe food allergies, safe and knowledgeable back-to-exercise guidance, sleep, biweekly housekeeping, signage for the house I.e “new baby, pls don’t ring the bell. Little hands touch our floor- leave your shoes at the door,. pls wash hands”. Hospital baby box (like in Finland!)
Night nanny(!!!!), meals, more postpartum visits with healthcare provider, pelvic floor PT, behavioral health support (ie therapy), house cleaning
Pelvic floor therapy being the norm would be nice! Lactation consultants automatically coming to your house would be so much easier than dragging your baby to the office/hospital. 
Help at home, financial, more time away from work
Postpartum doula who know so much about newborns, cranial sacrum therapy, Massage in home, Telehealth therapy, household task help, family and friends support, meal trains provided, lactation support
Meals, house cleaning, easily accessible support groups for lactation and newborn life, community for older siblings, paid time off from work for myself and partner.
Therapy, physical therapy (pelvic floor and anything else needed, SI joint pain in my pelvis was debilitating for me on and off for a couple years after my first). Meals/support with daily tasks, lactation support, physical check ups—it often felt like birthing parent was an afterthought to kid check ups. I had scary bleeding, internal stitches that were extremely painful and slow to heal (much slower than the external stitches), joint pain, etc and there was little to no care for me outside of what I advocated for. For my second physical injury was less (not zero), but postpartum depression was scary and “covered” therapy was EXPENSIVE. Shockingly expensive. To the point where it added stress and anxiety about getting it despite knowing it was necessary. 
Support groups, therapy, parenting classes, more doctors appointments for mom. 
Lactation consultants, postpartum doula, counseling, mom groups
In home help services - cooking and cleaning. Self care like relaxation and gym services 
Massage, pelvic PT, doula care postpartum, lactation support, therapy, postpartum yoga, pediatrician with flexible policies 
Ongoing in home visits, much greater medical follow up postpartum, mental health care, child care
Home nurse, in home lactation, longer family leave,in person  peer support groups, chiro/body work for mom and baby 
All of them
More mental health screaming, more feeding support, lactation/ breastfeeding support, longer maternity and paternity leave 
Night nurse, in home checkups for me and baby, meals
Immediate lactation support, doula, longer maternity/paternity leave, help around the house/cleaning/meals, pelvic floor therapy even without any apparent issues/injuries 
More help with breastfeeding and household help
In Home help, pelvic floor 
Naney, chef, house cleaner, more postpartum obgyn appts, lactation consultant, support for husband with PPD, car seat safety tech, 
1. Weekly recovery check ins from a doula or midwife. Nobody checked on my recovery at all during this time.
2. Lactation or formula consultation (nursing isn't possible for everyone and there is no info given about nursing alternatives)
3. Therapy for post partum depression/other complications covered by insurance
4. Pelvic floor PT. I had this and it was awesome and very necessary
5. New parents (mother's) groups through hospital and friends
6. 6 months paid maternity leave from work and discrimination protection/ramp up support upon return.
7. Discounted or tax deductible childcare. This is a no brainer. We don't even have guaranteed leave and childcare in my area runs about $25-50k a year per child depending on what you choose. Unless you have a lucrative job, it forces you to rethink whether you want to work at all. 
Professional cleaning, in person lactation, meal prep program, counseling, postpartum visit and contraception, post partum doula, nighttime assistance for sleep, pelvic floor PT, massage or chiropractic
Lactation, counseling, meals covered, laundry, in person new parents group
Pelvic floor therapy, household tasks, night nurse, couples therapy 
Doula, meals, massage, lactation consultant, PAID PATERNITY LEAVE, emotional support groups, pelvic floor therapy
Pelvic floor therapy, lactation support, talk therapy, help household chores 
Mental health support, more lactation support that wasn’t so expensive or far away. 
Therapy, PT, postpartum doula, housekeeper
Childcare, pelvic PT, housekeeping 
Lactation services, more frequent OBGYN appointments postpartum, meal and in home support especially at night, massage/acupuncture, access to pelvic floor therapy 
Help with household duties, help with baby, help with other children, PP classes on why we feel the way we do after 
Household tasks, emotional
Doula, babysitter, chiropractor, pelvic floor, lactation, counselor, sleep help, meals  
Physical Therapy 
Access to a mental health professional who specializes in postpartum would have been ideal. The medical professionals did not seem comfortable with this aspect of things and that felt isolating. I also did not know about half the things that I experienced in the fourth trimester so having information on how to even go to would have been helpful. You don’t know what you don’t know. And then, of course, you don’t even know what provider or resources to ask for. 
Financial support to take time off work, 
Lactation support that came to my house. Packing up a baby to go into the hospital during winter was not ideal. Family and friends who would be able to give you a break and a nap. Therapy appointments as needed to talk about PPD and PPA. 
I wish pelvic floor therapy was standard, household help (cooking, cleaning, groceries), emotional support (personal and professional therapy), in home services 
Pelvic floor, more medical follow-ups, additional feeding support, NICU parent support and birth trauma support 
Easy access to a professional to talk to about fears/anxiety/concerns postpartum. 
Paid time off + all items listed above 
Pelvic floor therapy, counseling, lactation support, childcare, love
Childcare, more maternity leave, sleep support, PT, nutrition, lactation consultant, meal support, housekeeping support
Emotional support/therapy, in home help for household chores, more in depth post partum care from OB (more than just a 6 week checkup) 
Lactation support. Therapy (mental & physical)
Emotional support, lactation support, in-home care help, pelvic floor education and rehab, if need be. 
Home help, real education of what to expect and more education on PPD. 
Physical therapy,  therapy and support around my postpartum anxiety.  help with household tasks.
Pelvic floor rehab, lactation support, in home care support, massage, therapy 
IBCLC visits, Pelvic floor therapist, in-home help with cleaning and child care (especially first 3 months), massage
I really need help with household tasks
Childcare so mom can sleep as much as possible (if she's nursing only she can feed the baby, but could sleep in between feedings or pump and then sleep); help with meals and laundry; someone to drive mom to medical appointments in the immediate postpartum period; someone to offer emotional support either in person or online
Night nurse, child care nurse, lactation
Paid leave for both birthing person and partner for a minimum of 12 weeks, in home postpartum care (homebirth model), access to support groups with childcare for older children, and greater community support for meals, and for older children’s needs. 
Chiro, massage, therapist, doula, pelvic floor support, more paternity leave for my husband, lactation support, more wellness checks on the mom
Therapy, house keeping, lactation support, pelvic floor therapy, longer maternity leave 
Meals provided, cleaning service, pelvic floor therapy, massages 
Physical rehab- pelvic floor pt, fully paid maternity leave, family support with child care, lactation support, social support 
Childcare, household tasks, social support with other parents, lactation (esp for exclusive pumping)
Lactation, mental health, paid family leave,
Childcare for other children 
Physical 
Assistance with household tasks, emotional support, lactation support, not having to return to work so quickly, subsidized childcare, pelvic floor therapy
I would want meals, house cleaning, and laundry help. Meals would be most important.
Mental health (post partum anxiety depression), lactation assistance, more paternity leave to alleviate strain on new mom, increased maternity leave, more education for other family members on how to better support new moms 
Any listed above! Anything! More lactation support. Support home with newborn first few nights. More clinic follow up. More mental health check it.
Parental leave, family coming, meals from friends, regular babysitting, therapy, lactation consultant, more dedicated mother care other than a single checkup at 6wk postpartum. (I had help from friends and family but the standard medical care basically ignores the mother once the baby's out other than very basic hospital care + one 6wk appointment.) Paid, standard postpartum therapy check-ins.
Lactation, childcare, meals, and mental health 
More follow ups for MY care, in-home visits
Meals made and served to me, weekly postpartum doula in-home visit to check-in on me mentally and emotionally and answer questions. 
I wish someone had asked me how I was feeling like they weren't just reading off a pamphlet. Feels like they just want you to say yes or no. Even when I did bring up my concerns with obgyn she scheduled a follow up for PPD but again it was like that person was reading off something. 
Emotional support, physical support in household tasks, support groups with new parents - virtually and in person, lactation support, parent education, sleep education, self care as a new mom
Paid leave
Pelvic floor therapy
Lactation support
Nutrition support
Mental health support
Someone to help with daily activities while healing and bonding with baby
Emotional and lactation support 
Physical therapy, emotional support, housekeeping, cooking meal prep, pelvic floor therapy.
Pelvic floor PT! It’s so hard to get in!! 
Postpartum doula, chiropractic, lactation consultant, in person support groups, pediatric dentists
Pelvic floor therapy, paid maternity leave, meal train
Childcare, cleaning, meals
Counseling, lactation, household help, physical therapy, childcare
Pelvic floor therapy, overnight care, childcare, sleep training, feeding support 
A nurse to come check on us at home, therapy, meals, cleaning, cooking, any and all help. Paid time off work for a year or more.
Night doula services, assistance with meals and home cleaning, lactation, pelvic floor physio, mental health support, in-person community (aka village) 
Pelvic floor rehab, acupuncture, therapy, more in home services in general , new parents group, paid time off from government, child care, more acceptance of formula milk
Postpartum doula to help with cooking, cleaning and all around support & personal connection in the first months. Standard dr checks for mom & baby, pelvic floor PT as part of standard care, check ins with a therapist as part of standard care, chiropractor and massage therapist to help ease your body into its new changed form. 
Household help, grocerieserrands, pt, lactation, emotional (option for therapy groups or individual), nutrition 
Practical support (cleaning, cooking), mental health support (counseling that wasn't so limited and difficult to access), lactation pumping education and reassurance when it wasn't successful, paid leave from work, more leave from work
Paid parental leave, lactation consultant, food made, baby sleep support, feeding support (BLW or purées), REAL PPD PPA screening (not those terrible surveys), night nurse
Pelvic floor. Lactation. Post partum doula. 
Longer mat leave, emotional support, more Check ins with the dr 
Lactation consultant, emotional support, pelvic floor rehab, wellness follow ups, and massage 
More followup appointments (later than 6 weeks), auto enrollment in pelvic floor PT, nurse home visits to help offer guidance & maybe watch newborn for a couple hours. Help connecting with other working parents. Food delivery. Child care. Longer parental leave. I could make a very long list.
Lactation, mental health, parenting support
Household chores, meals, talking, lactation and therapy 
One year paid leave (this would’ve been HUGE),  more parental leave for spouse, in-home lactation support, more frequent counseling. 
Lactation, in home support, meal deliveries, doula (night or pp)
1 year paid leave, in home support for newborn care, assistance with feeding newborn that is inclusive to any feeding method (judgment free), pelvic floor support and postpartum rehab 
Paid family leave; family that lived closer; mental health support for dads and moms 
Community, medical, mental and also more wrap around. Supports within work relative to flexible schedule, privacy sand ability to pump if that is desired. 
lactation support, night nurse, childcare
Lactation consultant, postpartum doula, meals, cleaning, emotional support to transition to motherhood, longer maternity leave. 
Non that weren’t listed 
New mom's group, meal train, cleaning help, night nanny
Lactation
Physical recovery help
Physical recovery products like pads
Postpartum support around the house
Help from family with older children 
All the things listed but most important would be paid family leave of at least 4 months minimum and access to safe affordable childcare
massage, chiro, pelvic floor pt, counseling, more than one postpartum follow up, community groups that are easy to find & connect with. 
Someone to come hold the baby while I napped, shower etc but more when he started moving bc the need exceeds the first 6 weeks, it’s now that he’s moving…. But massage, acupuncture, meal train, therapy, more pelvic floor therapy, baby and me yoga…. 
Therapy, paid parental leave, meals, community support, massage
More help with my older children 
Massage, chiropractic, pp doula care
Meal train, someone to talk to to profess the birth, in house lactation support, help with housework. 
In home help!! 
midwife, Friends, family, meal train, therapist, doula, baby groups, 
Emotional support, help with housework, pelvic floor help, lactation support
Pelvic floor PT, lactation support, in home postpartum care, emotional support therapy, more education on vaginal care postpartum 
Therapist, postpartum doula, bodywork, meal train, in home follow ups for months or even a year, acupuncture, pelvic floor PT, new parent group
Therapist, postpartum doula, bodywork, meal train, in home follow ups for months or even a year, acupuncture, pelvic floor PT, new parent group
Overnight doula, daytime support (for taking care of baby so I can do other things and have a break), therapeutic massage (I have had intense tension, pain, and numbness in my shoulders neck arms from holding and nursing baby), wholesome meals (I cook wholesome meals for us but it'd be nice to have someone else make delicious and nutritious meals sometimes [my family sometimes brings food but they don't necessarily have the knowledge and skill to make wholesome home-cooked meals])
Monthly massages, therapy, lactation consultant, doula visits, paid leave (!!!)
EASILY accessible lactation support, planned in advance (it was a struggle to find insurance covered lactation support, and even worse to do it after babies were born), postpartum doula, in home emotional support, immediate household help for meals, cleaning, bottle prep, overnight relief to be able to sleep or rest, assistance to be able to leave the house, pelvic floor therapy and physical movement therapy (I could not even walk after my twins were born, because my core was so destroyed, and even the hospital didn’t know how to help). 
Didn't necessarily need more care but easier access to it. 
Home visits from lactation consultants, pediatrician; pelvic floor therapy; nutrition wellness support 
someone to come over daily to help with keeping the house in order and being there so i could nap rest.  
Therapy, therapy, bodywork and therapy.
Personal time
For starters insurance covered homebirth, midwives,   Birth and postpartum doula, postpartum yoga, acupuncture, chiropractor, therapist, pelvic floor therapy, nutritional guidance for me and baby, grocery delivery service, pre baby friends to stick around…family support, linger maternity and paternity leave
Therapy (mental health) for me and partner
Physical therapy with pelvic floor specialty but also general recovery and strength training
Postpartum support group with facilitation 
Dad’s support group with facilitation
In home midwife checkups 
Lactation counseling
Tongue tie evaluation if suspected
Body work
In home household support (cooking, laundry, cleaning, childcare)
Minimum six months fully paid leave for both parents—longer better
Postpartum prep class with partner")
```

```{r}
corpus <- Corpus(VectorSource(comments_text))
corpus_clean <- corpus %>%
   tm_map(content_transformer(tolower)) %>% 
  tm_map(removePunctuation) %>%
  
  tm_map(removeNumbers) %>% 
  tm_map(removeWords, stopwords("en")) %>%
  tm_map(stripWhitespace) %>% 
  tm_map(removeWords, c("support", "postpartum"))

tdm <- TermDocumentMatrix(corpus_clean)

m <- as.matrix(tdm)

word_freqs <- sort(rowSums(m), decreasing = TRUE)

word_freq_table <- data.frame(word = names(word_freqs), freq = word_freqs)

colors <- viridis(nrow(word_freq_table), option = "D")

wordcloud2(word_freq_table, size = 0.5, color = colors)

```


### Plot 5: Heat map
#### Data cleanup steps specific to plot 4

```{r heatmap-like-for-plot-critique}
# comparing states and support_type

p2 <- Postpartum <- Postpartum |>
  filter(support_type != "NA") |>
  filter(regions != "NA")
  
ggplot(Postpartum, aes(x = support_type, y = regions, fill = support_type)) +
   geom_tile(alpha = .7) +
  scale_fill_viridis_d() +
  theme_minimal() +
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
 # theme(axis.text.y=element_blank(),
       # axis.ticks.y=element_blank()) +
  labs(title = "Heatmap-Like Plot Example", y = "US Regions", fill = "Support Type")

ggsave("example-tile-heatmap-wide.png", width = 10, height = 5)

```


### Plot 6: TBD

#### Data cleanup steps specific to plot 5

```{r cost-factor-cleanup}

yes_cost_a_factor <- c("I received care from friends and family, had I not had that I wouldn’t have been able to afford to pay for postpartum care services","To some extent, but luckily I could afford almost whatever I wanted/needed.","We strongly considered going to a birth center for my first birth, but they did not accept insurance and it was cost prohibitive. I feel we would have had more postpartum support with my first if we had gone that route.","Had already paid max out of pocket w labor","No referral","lactation specialist not covered, couldn’t afford otherwise","I definitely knew to look for support covered by insurance.","Did on seek in home help due to cost", "Did on seek in home help due to cost","Partially. Had i known there was support, I probably couldnt afford it.", "Yes but we had a generous budget and family to help financially","Unsure of question.... did it cost,  some of it did", "It was definitely a luxury to afford therapist and lactation help but anything other than that I viewed as “extra.”", "No doula $", "Yes but not as much as just not knowing it was available", "If I could afford food delivery, laundry service, etc, I would have hired the help!", "Do not have insurance","Cost to an extent but also Covid played a role- birth in December 2019, brought son home from NICU in 2020 and recovery was long into 2020)", "Copays sometimes.", "Yes in terms of acupuncture etc I didn’t budget for it and wish I did", "My husband and I prioritized Postpartum care highly so yes and no")

cost_not_a_factor <- c("It was more not knowing what services I should have had access to. I know more know with Instagram follows.", "No. I just was unaware of the services that might be helpful. If I had another kid I’d invest in more.", "Covid was, not cost", "Not since we hit our deductible", "Main factor was pandemic. 6 week was nearly canceled, counseling went virtual but took months to initiate")

cost_not_applicable <- c("Did not know post partum services other than the follow up appointment were covered services", "Didn’t even know what type of support was available because no one told me!","The pandemic significantly impacted my lack of access to postpartum support, especially in-person support", "I don't know, I wasn't aware of many services")


#Postpartum_Experience_renamed_variables_US %>% 
 # mutate(cost_factor = case_when(cost_factor %in% yes_cost_a_factor ~ "Yes",
                                     # cost_factor %in% cost_not_a_factor ~ "No",
                                     # cost_factor %in% cost_not_applicable ~ "N/A",
       #   TRUE ~ cost_factor))

```


### Plot 7: Missing Data

```{r missing data plot}
Postpartum <- Postpartum %>%
  select(respondent, state, age, birth_location, informed_by, other_info_sources, support_type, provider, ins_covered_services, cost_factor, if_insurance, critical_support, ideal_support, comments, emails)
```

```{r}
vis_miss(Postpartum)

ggsave(filename = "Missingdataplot.png", width = 8, height = 4)
```


#### Final Plot 1

```{r}

```


### Plot 2: _________

### Plot 3: ___________

Add more plot sections as needed. Each project should have at least 3 plots, but talk to me if you have fewer than 3.

### Plot 4: ___________ 

